# Part 1: Introduction

```{r intro}
load("../data/fin2.Rdata")
introData <- intro(fin2)
```

What features make for a popular film? For the purposes if this analysis, popular is defined strictly by box office success. Sampling over 5,000 movies, the mean domestic box office was approximately \$`r round(introData$stats$Mean,-2)`, with half earning approximately \$`r round(introData$stats$Median, -2)`,  The top 5 films observed (`r kfigr::figr(label = "top5films", prefix = TRUE, link = TRUE, type="Table")`) earned an average of \$`r round(mean(introData$WorldWide), -2)` worldwide!

`r kfigr::figr(label = "top5films", prefix = TRUE, link = TRUE, type="Table")` Top 5 films at the box office
```{r top5films}
knitr::kable(introData$top5, format.args = list(big.mark = ",")) %>%
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

What is it about these films that make them so successful? The analysis explores this question from the perspective of a studio executive at the nascient stages of a film production. The purpose, therefore, is to render insight that might inform the key decisions early decisions that most impact success at the box office.


* * *
