# Part 1: Introduction

```{r intro}
load("../data/fin2.Rdata")
introData <- intro(fin2)
```

What features make for a popular film at the box office? The mean domestic box office, for a sample of over 5000 films, was approximately \$`r round(introData$stats$Mean,-2)`, with half earning approximately \$`r round(introData$stats$Median, -2)`,  The top 5 films observed (`r kfigr::figr(label = "top5films", prefix = TRUE, link = TRUE, type="Table")`) earned an average of \$`r round(mean(introData$top5$Domestic), -2)`!

<div class = "col2-right">
`r kfigr::figr(label = "top5films", prefix = TRUE, link = TRUE, type="Table")` Top 5 films at the box office
```{r top5films}
knitr::kable(introData$top5, format.args = list(big.mark = ","), 'html') %>%
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = F, position = "float_right")
```
</div>
<div class = "col2-left">
What is it about these films that make them so successful? The analysis explores this question from the perspective of a studio executive at the nascent stages of a film's production. Applying linear regression techniques to data obtained the IMDb, Rotten Tomatoes and BoxOfficeMojo websites, the aim was to render insights that might inform the key early decisions that studio executives, producers and directors must make to have the greatest positive impact at the box office.
</div>   

* * *
