```{r restore-data}
# fin1 <- openxlsx::read.xlsx(xlsxFile = "../data/sample.xlsx")
# fin2 <- openxlsx::read.xlsx(xlsxFile = "../data/financials.xlsx")
# save(fin1, file = "../data/fin1.Rdata")
# save(fin2, file = "../data/fin2.Rdata")
```


```{r load-data}
rerun <- FALSE
load("../data/movies.Rdata")
load("../data/fin1.Rdata")
load("../data/fin2.Rdata")
```

```{r preprocess}
# dataSets  <- preprocess(movies, fin1, fin2)
# train <- dataSets$train
# test <- dataSets$test
# case <- dataSets$case
# mdb2 <- dataSets$mdb2
# save(train, file = "../data/train.RData")
# save(test, file = "../data/test.RData")
# save(case, file = "../data/case.RData")
# save(mdb2, file = "../data/mdb2.RData")
# rerun <- TRUE
```



```{r reload-data}
load("../data/train.Rdata")
load("../data/test.Rdata")
load("../data/case.Rdata")
load("../data/mdb2.Rdata")
```


# Part 2: Data
The data were comprised of audience and critics opinions, awards, studio, and actor information from Rotten Tomatoes, imdb, and BoxOfficeMojo.com for a random sample of 651 movies produced and released prior to 2016.

## Data Sources
### Rotten Tomatoes
Launched in August 1998 by Senh Duong, Rotten Tomatoes is an American review aggregation website for film and television.

### IMDB

## Generalizability

## Data Preprocessing
As a first step, variables such as website addresses and film titles were removed from the data set, then some 619 completed cases were extracted for downstream analysis. Since the focus was on theatrical releases, TV movies were excised from the data set. Next, three additional data sets were created:
* Film Daily Box Office
* Director Profiles
* Actor Profiles

**Film Daily Box Office**
The overarching aim was to understand which factors most influenced  box office success for a film. Since  box office revenue was not among the features provided in the data set, the first preprocessing step was to identify (or create) a response variable that would correlate with  box office success. As such, total  box office was obtained from the BoxOfficeMojo.com site for a random sampling of some `r round(nrow(mdb2), -1)` films from the original sample. The first step in the bivariate analysis was to identify which of the provided variables (or variables derived from those provided) most correlated with  box office success.

**Director / Actor Profiles:**
The purpose of the director/actor profiles was to capture the experience and popularity of each director and actor. The experience variables were simply the total number of films in the sample in which the director or actor was listed in the original sample.  Popularity, in the director's case was the sum of the IMDB votes for the director's films.  Similarly, the popularity for an actor was the sum of the *allocated* IMDB votes for films in which the actor was listed as one of the top 5. Actors were allocated IMDB votes as follows:
* 40% of total film IMDB votes for actor1
* 30% of total film IMDB votes for actor2
* 15% of total film IMDB votes for actor3
* 10% of total film IMDB votes for actor4
* 5% of total film IMDB votes for actor5
These variables were then merged into the main sample data set.

**Variables Added**
A variable was created to capture the number of days between theatrical and dvd release. A composite score variable defined as 10 * IMDB Rating + critics score + audience_score was created and lastly, log transformations were applied to certain variables such as IMDB and cast votes. To sum, the following variables listed in `r kfigr::figr(label = "derived", prefix = TRUE, link = TRUE, type="Table")` were added to the data set.
`r kfigr::figr(label = "derived", prefix = TRUE, link = TRUE, type="Table")`: Variables added to the data set
```{r derived}
raw <- openxlsx::read.xlsx(xlsxFile = "../data/features.xlsx")
derived <- raw %>% filter(Source == "Derived") %>% select(Variable, Description) %>% arrange(Variable)
knitr::kable(derived) %>%
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

**Variables Removed**
The following variables listed in `r kfigr::figr(label = "removed", prefix = TRUE, link = TRUE, type="Table")` were removed from the data set for the reasons listed below.
`r kfigr::figr(label = "removed", prefix = TRUE, link = TRUE, type="Table")`: Variables removed from the data set
```{r removed}
raw <- openxlsx::read.xlsx(xlsxFile = "../data/features.xlsx")
removed <- raw %>% filter(uni == "no") %>% select(Variable, Description, Rationale) %>% arrange(Variable)
knitr::kable(removed) %>%
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

The full resultant codebook for the data set can be found in Appendix A

* * *
