# Part 5: Modeling
The aim at this stage was to develop two prediction models:  Model One, a multiregression model that predicts the log of IMDB votes, and Model Two, a simple linear regression model that predicts log box office revenue based upon the log of IMDB votes. The former was the best performing of four multiregression models, developed using both forward selection and backward elimination method selection methods.  These four models and their model selection methods were:  

`r kfigr::figr(label = "models", prefix = TRUE, link = TRUE, type="Table")`: Multiregression prediction models
```{r models}
models <- openxlsx::read.xlsx(xlsxFile = "../data/models.xlsx")
knitr::kable(models, digits = 2) %>%
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

The remainder of this sections is organized as follows.  

1. Model One: Multiregression Model  
1.1. Model Selection Methods  
1.2. Full Model  
1.3. Model Alpha  
1.4. Model Beta  
1.5. Model Gamma  
1.6. Model Delta  
1.7. Model Comparison  
1.8. Model Two: Final Multiregression Model   
   
2. Model Two: Simple Linear Regression Model   
2.1. Model Overview    
2.2. Model Diagnostics     
   
3. Model Summary  

## Model One: Multiple Linear Regression
Model One was the best performing of models Alpha, Beta, Gamma, and Delta. The following provides an overview of the model selection methods used, then each model is described and diagnosed vis-a-vis assumptions of linearity, homoscedasticity, normality of errors, multicollinearity, and the treatment of influential points.

### Model Selection Methods
Both forward selection and backward elimination model selection techniques were used. The forward selection approach optimized adjusted r-squared; whereas the backward elimination method was based upon p-values.

#### Forward Selection
The forward selection process began with a null model then all variables were added to the model, one-by-one, and the model which provided the greatest improvement over the current best adjusted R-squared was selected. The process repeated with each variable that was not already in the model until all variables were analyzed. Only the models that improved adjusted r-squared were retained at each step. 

#### Backward Elimination
The backward elimination approach began with the full model. A regression analysis was performed and the least significant predictor (that with the highest p-value) was removed from the model.  This process repeated, removing only the most least significant predictor at each step, until all predictors had p-values below the designated $\alpha = .05$ threshold.   

### Full Model Selection
The motivation for this analysis was provide insight to inform the decisions studio executives must make at the early stages of a film project. That said, the variables selected for the full model were those that are *"knowable"*  by studio executives before theatrical release. Consequently variables excluded from consideration as predictors consist of:  
* variables not "knowable" at project inception. This would include film ratings, scores, academy awards, and box office results
* variables that are redundant with other variables with higher correlations with the dependent variable.
* categorical variables with levels containing fewer than 5 observations, such as the actor, director and studio variables
* dvd release dates as dvd sales are out of the scope of this analysis.

As such, the full model is presented in `r kfigr::figr(label = "fullModel", prefix = TRUE, link = TRUE, type="Table")`.

`r kfigr::figr(label = "fullModel", prefix = TRUE, link = TRUE, type="Table")`: Variables in Full Model
```{r fullModel}
full <- openxlsx::read.xlsx("../data/features.xlsx")
full <- full  %>% filter(c == "yes" & Context == "Explanatory") %>% select(Type, Variable, Description) %>% arrange(Type, Variable)
knitr::kable(full, digits = 2) %>%
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")     
```

The following sections explore various models, model selection techniques, and model diagnostics. Comparisons were conducted and the models were evaluated on test data for prediction accuracy and stability. Lastly, the best performing model is selected and described on detail.   

### Model Alpha
For this model, a forward selection procedure was undertaken based upon the full model described above. `r kfigr::figr(label = "model_a_build", prefix = TRUE, link = TRUE, type="Table")` lists the variables in the order in which they were added.

`r kfigr::figr(label = "model_a_build", prefix = TRUE, link = TRUE, type="Table")`: Model Alpha forward selection process
```{r model_a_build, results = "html"}
# Obtain Data
mData <- process(train, stage = "m", y = "imdb_num_votes_log")  

# Perform forward selection
m <- forward(data = mData$full, y = "imdb_num_votes_log")

# Conduct regression analysis
modelA <- regressionAnalysis(mod = m, mName = "Model Alpha", yVar  = 'imdb_num_votes_log',
                               yLab = "Log IMDB Votes")

# Report regression steps
knitr::kable(modelA$build, digits = 2) %>%
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

As indicated in `r kfigr::figr(label = "modelA_overview", prefix = TRUE, link = TRUE, type="Table")`  and graphically depicted in `r kfigr::figr(label = "modelA_regression", prefix = TRUE, link = TRUE, type="Figure")`, `r modelA$comments$apa`

`r kfigr::figr(label = "modelA_overview", prefix = TRUE, link = TRUE, type="Table")`: Model Alpha  Summary Statistics
```{r modelA_overview}
knitr::kable(modelA$glance, digits = 3) %>%
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```


```{r modelA_regression}
modelA$plots$regression
```
`r kfigr::figr(label = "modelA_regression", prefix = TRUE, link = TRUE, type="Figure")` Model Alpha Regression


#### Model Diagnostics
##### Linearity
The linearity of each predictor with the log number of IMDB votes is illustrated in `r kfigr::figr(label = "modelA_linearity", prefix = TRUE, link = TRUE, type="Figure")`.  

```{r modelA_linearity, fig.height=10}
library(gridExtra)
n <- length(modelA$plots$linearity)
nCol <- floor(sqrt(n))
```
`r kfigr::figr(label = "modelA_linearity", prefix = TRUE, link = TRUE, type="Figure")` Model Alpha linearity plots

`r modelA$comment$linearity`

##### Homoscedasticity
The following plot (`r kfigr::figr(label = "modelA_homoscedasticity", prefix = TRUE, link = TRUE, type="Figure")`) of the residuals versus the fitted values provides a graphic indication of the distribution of residual variances. 
```{r modelA_homoscedasticity}
modelA$plots$res_fitted
```
`r kfigr::figr(label = "modelA_homoscedasticity", prefix = TRUE, link = TRUE, type="Figure")` Model Alpha homoscedasticity plot

`r modelA$comments$homoscedasticity`

##### Residuals
The histogram and the normal Q-Q plot in `r kfigr::figr(label = "modelA_residuals", prefix = TRUE, link = TRUE, type="Figure")` illustrate the distribution of residuals.

```{r modelA_residuals}
gridExtra::grid.arrange(modelA$plots$res_hist, modelA$plots$res_qq, ncol = 2)
                        

```
`r kfigr::figr(label = "modelA_residuals", prefix = TRUE, link = TRUE, type="Figure")` Model Alpha residuals plot

`r modelA$comments$normality`

##### Multicollinearity
As shown in `r kfigr::figr(label = "modelA_multicollinearity", prefix = TRUE, link = TRUE, type="Figure")` and `r kfigr::figr(label = "modelA_vif", prefix = TRUE, link = TRUE, type="Table")`, `r modelA$comments$collinearity`
```{r modelA_multicollinearity}
modelA$plots$multicollinearity$plot()
```
`r kfigr::figr(label = "modelA_multicollinearity", prefix = TRUE, link = TRUE, type="Figure")`: Model Alpha correlations among quantitative predictors 

`r kfigr::figr(label = "modelA_vif", prefix = TRUE, link = TRUE, type="Table")` Model Alpha variance inflation Factors
```{r modelA_vif}
knitr::kable(modelA$tests$collinearity, digits = 3) %>%
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

##### Outliers
```{r modelA_outliers}
gridExtra::grid.arrange(modelA$plots$res_leverage, modelA$plots$cooks, ncol = 2)
```
`r kfigr::figr(label = "modelA_outliers", prefix = TRUE, link = TRUE, type="Figure")` Model Alpha Outliers

`r modelA$comments$outliers` The discern the effect of these outliers on the model, a new model (Model B) was created without the outliers removed.

### Model Beta
This was also a forward selecion model; however, it was based upon the full model with **outliers from Model Alpha removed**. The variables were added as described in  `r kfigr::figr(label = "model_b_build", prefix = TRUE, link = TRUE, type="Table")`

`r kfigr::figr(label = "model_b_build", prefix = TRUE, link = TRUE, type="Table")`: Model Beta forward selection process
```{r model_b_build, results = "html"}
# Obtain Data
mData <- process(train, stage = "m", "imdb_num_votes_log", outliers = modelA$tests$influential)  

# Perform forward selection
m <- forward(mData$full, y = "imdb_num_votes_log")

# Conduct regression analysis
modelB <- regressionAnalysis(m, mName = "Model Beta", yVar  = 'imdb_num_votes_log',
                               yLab = "Log IMDB Votes")

# Report regression stesp
knitr::kable(modelB$build, digits = 2) %>%
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

As indicated in `r kfigr::figr(label = "modelB_overview", prefix = TRUE, link = TRUE, type="Table")`  and graphically depicted in `r kfigr::figr(label = "modelB_regression", prefix = TRUE, link = TRUE, type="Figure")`, `r modelB$comments$apa`

`r kfigr::figr(label = "modelB_overview", prefix = TRUE, link = TRUE, type="Table")`: Model Beta Summary Statistics
```{r modelB_overview}
knitr::kable(modelB$glance, digits = 3) %>%
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

```{r modelB_regression}
modelB$plots$regression
```
`r kfigr::figr(label = "modelB_regression", prefix = TRUE, link = TRUE, type="Figure")` Model Beta Regression

#### Model Diagnostics
##### Linearity
The linearity of each predictor with the log number of IMDB votes is illustrated in `r kfigr::figr(label = "modelB_linearity", prefix = TRUE, link = TRUE, type="Figure")`.  

```{r modelB_linearity, fig.height=10}
n <- length(modelB$plots$linearity)
nCol <- floor(sqrt(n))
```
`r kfigr::figr(label = "modelB_linearity", prefix = TRUE, link = TRUE, type="Figure")` Model Beta linearity plots

`r modelB$comment$linearity`

##### Homoscedasticity
The following plot (`r kfigr::figr(label = "modelB_homoscedasticity", prefix = TRUE, link = TRUE, type="Figure")`) of the residuals versus the fitted values provides a graphic indication of the distribution of residual variances. 
```{r modelB_homoscedasticity}
modelB$plots$res_fitted
```
`r kfigr::figr(label = "modelB_homoscedasticity", prefix = TRUE, link = TRUE, type="Figure")` Model Beta homoscedasticity plot

`r modelB$comments$homoscedasticity`

##### Residuals
The histogram and the normal Q-Q plot in `r kfigr::figr(label = "modelB_residuals", prefix = TRUE, link = TRUE, type="Figure")` illustrate the distribution of residuals.

```{r modelB_residuals}
gridExtra::grid.arrange(modelB$plots$res_hist, modelB$plots$res_qq, ncol = 2)
                        

```
`r kfigr::figr(label = "modelB_residuals", prefix = TRUE, link = TRUE, type="Figure")` Model Beta residuals plot

`r modelB$comments$normality`

##### Multicollinearity
As shown in `r kfigr::figr(label = "modelB_multicollinearity", prefix = TRUE, link = TRUE, type="Figure")` and `r kfigr::figr(label = "modelB_vif", prefix = TRUE, link = TRUE, type="Table")`, `r modelB$comments$collinearity`
```{r modelB_multicollinearity}
modelB$plots$multicollinearity$plot()
```
`r kfigr::figr(label = "modelB_multicollinearity", prefix = TRUE, link = TRUE, type="Figure")`: Correlations among quantitative predictors 

`r kfigr::figr(label = "modelB_vif", prefix = TRUE, link = TRUE, type="Table")` Model Beta Variance Inflation Factors
```{r modelB_vif}
knitr::kable(modelB$tests$collinearity, digits = 3) %>%
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

Upon further analysis, the high VIF for genre and MPAA rating was a consequence of the reference categories having a small proportion of the overall cases. The reference category for genre, Action & Adventure, had just `r nrow(subset(train, genre == "Action & Adventure"))` films, `r round(nrow(subset(train, genre == "Action & Adventure")) / nrow(train) * 100, 1)`% of the cases. The reference category for MPAA rating was G, consisting of `r nrow(subset(train, mpaa_rating == "G"))` observations, `r round(nrow(subset(train, mpaa_rating == "G")) / nrow(train) * 100, 1)`% of the cases. Though the p-values for the indicator variables may be high, the overall test that all indicators have coefficients of zero is unaffected by the high VIFs

##### Outliers
```{r modelB_outliers}
gridExtra::grid.arrange(modelB$plots$res_leverage, modelB$plots$cooks, ncol = 2)
```
`r kfigr::figr(label = "modelB_outliers", prefix = TRUE, link = TRUE, type="Figure")` Model Beta Outliers

`r modelB$comments$outliers` A case-wise review of the influential points did not reveal any data quality issues; therefore, the influential points would not be removed from the model.

### Model Gamma
For this model, a backward elimination procedure was undertaken based upon the full model  The variables were removed as described in  `r kfigr::figr(label = "model_c_build", prefix = TRUE, link = TRUE, type="Table")`

`r kfigr::figr(label = "model_c_build", prefix = TRUE, link = TRUE, type="Table")`: Model Gamma
```{r model_c_build, results = "html"}
# Obtain Data
mData <- process(train, stage = "m", "imdb_num_votes_log")  

# Perform forward selection
m <- back(mData$full, y = "imdb_num_votes_log", alpha = 0.05)

# Conduct regression analysis
modelC <- regressionAnalysis(m, mName = "Model Gamma", yVar  = 'imdb_num_votes_log',
                               yLab = "Log IMDB Votes")

# Report regression stesp
knitr::kable(modelC$build, digits = 2) %>%
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

The model therefore retained the following variables:  

`r kfigr::figr(label = "modelC_variables", prefix = TRUE, link = TRUE, type="Table")` Model Gamma Variables
```{r modelC_variables}
vars <- openxlsx::read.xlsx(xlsxFile = "../data/features.xlsx")
vars <- vars %>% filter(Variable %in% m$selected) %>% select(Variable, Description)
knitr::kable(vars, digits = 3) %>%
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

As indicated in `r kfigr::figr(label = "modelC_overview", prefix = TRUE, link = TRUE, type="Table")`  and graphically depicted in `r kfigr::figr(label = "modelC_regression", prefix = TRUE, link = TRUE, type="Figure")`, `r modelC$comments$apa`

`r kfigr::figr(label = "modelC_overview", prefix = TRUE, link = TRUE, type="Table")` Model Gamma Summary Statistics
```{r modelC_overview}
knitr::kable(modelC$glance, digits = 3) %>%
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

```{r modelC_regression}
modelC$plots$regression
```
`r kfigr::figr(label = "modelC_regression", prefix = TRUE, link = TRUE, type="Figure")` Model Gamma Regression

#### Model Diagnostics
##### Linearity
The linearity of each predictor with the log number of IMDB votes is illustrated in `r kfigr::figr(label = "modelC_linearity", prefix = TRUE, link = TRUE, type="Figure")`.  

```{r modelC_linearity, fig.height=10}
n <- length(modelC$plots$linearity)
nCol <- floor(sqrt(n))
```
`r kfigr::figr(label = "modelC_linearity", prefix = TRUE, link = TRUE, type="Figure")` Model Gamma linearity plots

`r modelC$comment$linearity`

##### Homoscedasticity
The following plot (`r kfigr::figr(label = "modelC_homoscedasticity", prefix = TRUE, link = TRUE, type="Figure")`) of the residuals versus the fitted values provides a graphic indication of the distribution of residual variances. 
```{r modelC_homoscedasticity}
modelC$plots$res_fitted
```
`r kfigr::figr(label = "modelC_homoscedasticity", prefix = TRUE, link = TRUE, type="Figure")` Model Gamma homoscedasticity plot

`r modelC$comments$homoscedasticity`

##### Residuals
The histogram and the normal Q-Q plot in `r kfigr::figr(label = "modelC_residuals", prefix = TRUE, link = TRUE, type="Figure")` illustrate the distribution of residuals.

```{r modelC_residuals}
gridExtra::grid.arrange(modelC$plots$res_hist, modelC$plots$res_qq, ncol = 2)
                        

```
`r kfigr::figr(label = "modelC_residuals", prefix = TRUE, link = TRUE, type="Figure")` Model Gamma residuals plot

`r modelC$comments$normality`

##### Multicollinearity
As shown in `r kfigr::figr(label = "modelC_multicollinearity", prefix = TRUE, link = TRUE, type="Figure")` and `r kfigr::figr(label = "modelC_vif", prefix = TRUE, link = TRUE, type="Table")`, `r modelC$comments$collinearity`
```{r modelC_multicollinearity}
modelC$plots$multicollinearity$plot()
```
`r kfigr::figr(label = "modelC_multicollinearity", prefix = TRUE, link = TRUE, type="Figure")`: Correlations among quantitative predictors 

`r kfigr::figr(label = "modelC_vif", prefix = TRUE, link = TRUE, type="Table")` Model Gamma Variance Inflation Factors
```{r modelC_vif}
knitr::kable(modelC$tests$collinearity, digits = 3) %>%
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

##### Outliers
```{r modelC_outliers}
gridExtra::grid.arrange(modelC$plots$res_leverage, modelC$plots$cooks, ncol = 2)
```
`r kfigr::figr(label = "modelC_outliers", prefix = TRUE, link = TRUE, type="Figure")` Model Gamma Outliers

`r modelC$comments$outliers` To discern the effect of the influential points on the model, a new model (Model Delta) was created without the influential points of this model.


### Model Delta
This was also a backward elimination model; however, it was based upon the full model with **outliers from Model Gamma removed**.   The variables were removed as described in  `r kfigr::figr(label = "model_d_build", prefix = TRUE, link = TRUE, type="Table")`

`r kfigr::figr(label = "model_d_build", prefix = TRUE, link = TRUE, type="Table")`: Model Delta
```{r model_d_build, results = "html"}
# Obtain Data
mData <- process(train, stage = "m", "imdb_num_votes_log", outliers = modelC$tests$influential)  

# Perform forward selection
m <- back(mData$full, y = "imdb_num_votes_log", alpha = 0.05)

# Conduct regression analysis
modelD <- regressionAnalysis(m, mName = "Model Delta", yVar  = 'imdb_num_votes_log',
                               yLab = "Log IMDB Votes")

# Report regression stesp
knitr::kable(modelD$build, digits = 2) %>%
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

The model therefore retained the following variables:  

`r kfigr::figr(label = "modelD_variables", prefix = TRUE, link = TRUE, type="Table")` Model Delta Variables
```{r modelD_variables}
vars <- openxlsx::read.xlsx(xlsxFile = "../data/features.xlsx")
vars <- vars %>% filter(Variable %in% m$selected) %>% select(Variable, Description)
knitr::kable(vars, digits = 3) %>%
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```


As indicated in `r kfigr::figr(label = "modelD_overview", prefix = TRUE, link = TRUE, type="Table")`  and graphically depicted in `r kfigr::figr(label = "modelD_regression", prefix = TRUE, link = TRUE, type="Figure")`, `r modelD$comments$apa`

`r kfigr::figr(label = "modelD_overview", prefix = TRUE, link = TRUE, type="Table")`
```{r modelD_overview}
knitr::kable(modelD$glance, digits = 3) %>%
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```


```{r modelD_regression}
modelD$plots$regression
```
`r kfigr::figr(label = "modelD_regression", prefix = TRUE, link = TRUE, type="Figure")` Model Delta Regression


#### Model Diagnostics
##### Linearity
The linearity of each predictor with the log number of IMDB votes is illustrated in `r kfigr::figr(label = "modelD_linearity", prefix = TRUE, link = TRUE, type="Figure")`.  

```{r modelD_linearity, fig.height=10}
n <- length(modelD$plots$linearity)
nCol <- floor(sqrt(n))
```
`r kfigr::figr(label = "modelD_linearity", prefix = TRUE, link = TRUE, type="Figure")` Model Delta linearity plots

`r modelD$comment$linearity`

##### Homoscedasticity
The following plot (`r kfigr::figr(label = "modelD_homoscedasticity", prefix = TRUE, link = TRUE, type="Figure")`) of the residuals versus the fitted values provides a graphic indication of the distribution of residual variances. 
```{r modelD_homoscedasticity}
modelD$plots$res_fitted
```
`r kfigr::figr(label = "modelD_homoscedasticity", prefix = TRUE, link = TRUE, type="Figure")` Model Delta homoscedasticity plot

`r modelD$comments$homoscedasticity`

##### Residuals
The histogram and the normal Q-Q plot in `r kfigr::figr(label = "modelD_residuals", prefix = TRUE, link = TRUE, type="Figure")` illustrate the distribution of residuals.

```{r modelD_residuals}
gridExtra::grid.arrange(modelD$plots$res_hist, modelD$plots$res_qq, ncol = 2)
                        

```
`r kfigr::figr(label = "modelD_residuals", prefix = TRUE, link = TRUE, type="Figure")` Model Delta residuals plot

`r modelD$comments$normality`

##### Multicollinearity
As shown in `r kfigr::figr(label = "modelD_multicollinearity", prefix = TRUE, link = TRUE, type="Figure")` and `r kfigr::figr(label = "modelD_vif", prefix = TRUE, link = TRUE, type="Table")`, `r modelD$comments$collinearity`
```{r modelD_multicollinearity}
modelD$plots$multicollinearity$plot()
```
`r kfigr::figr(label = "modelD_multicollinearity", prefix = TRUE, link = TRUE, type="Figure")`: Correlations among quantitative predictors 

`r kfigr::figr(label = "modelD_vif", prefix = TRUE, link = TRUE, type="Table")` Model Delta Variance Inflation Factors
```{r modelD_vif}
knitr::kable(modelD$tests$collinearity, digits = 3) %>%
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```


##### Outliers
```{r modelD_outliers}
gridExtra::grid.arrange(modelD$plots$res_leverage, modelD$plots$cooks, ncol = 2)
```
`r kfigr::figr(label = "modelD_outliers", prefix = TRUE, link = TRUE, type="Figure")` Model Delta Outliers

`r modelD$comments$outliers` A case-wise review of the influential points did not reveal any data quality issues; therefore, the influential points would not be removed from the model.

### Model Comparisons
To summarize, models Alpha and Beta were constructed using forward selection and models Gamma and Delta were developed via backward elimination.  Models Beta and Delta were fitted without the influential data points from models Alpha and Gamma respectively.

`r kfigr::figr(label = "model_comparison", prefix = TRUE, link = TRUE, type="Table")` Summary of models
```{r model_comparison}
# Compare models
abcd <- rbind(modelA$glance, modelB$glance, modelC$glance, modelD$glance)
knitr::kable(abcd, digits = 3) %>%
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

#### Forward Selection vs. Backward Elimination
The differences in root mean square error for the models was not significant  `r round((abcd$RMSE[3] - abcd$RMSE[1]) / abcd$RMSE[3] * 100, 2)`% and `r round((abcd$RMSE[2] - abcd$RMSE[4]) / abcd$RMSE[4] * 100, 2)`%.  Similarly, the differences in adjusted R-squared were `r round((abcd[1,9] - abcd[3,9]) / abcd[3,9] * 100, 2)`% and `r round((abcd[4,9] - abcd[2,9]) / abcd[2,9] * 100, 2)`%, not a significant difference. Lastly the differences in the percent variance explained by the models also lacking in significance (`r round((abcd[3,11] - abcd[1,11]) / abcd[1,11] * 100, 2)`% and `r round((abcd[4,11] - abcd[2,11]) / abcd[2,11] * 100, 2)`%).

#### Influential Points: Drop or Not
The Beta and Delta models were trained on data sans the influential points from Alpha and Gamma.  The differences in RMSE (`r round((abcd$RMSE[1] - abcd$RMSE[2]) / abcd$RMSE[2] * 100, 2)`% and `r round((abcd$RMSE[3] - abcd$RMSE[4]) / abcd$RMSE[4] * 100, 2)`%) were insignificant, as were the differences in adjusted R-squared (`r round((abcd[2,9] - abcd[1,9]) / abcd[1,9] * 100, 2)`% and `r round((abcd[4,9] - abcd[3,9]) / abcd[3,9] * 100, 2)`%), and the percent of variance explained (`r round((abcd[2,11] - abcd[1,11]) / abcd[1,11] * 100, 2)`% and `r round((abcd[4,11] - abcd[3,11]) / abcd[3,11] * 100, 2)`%). However, a case-wise review of the influential points did not reveal any data quality issues; therefore, the points would not be removed.

#### Prediction Accuracy
The evaluate the effects of model selection method and the treatment of outliers on prediction accuracy, the four multiregression models were evaluated for prediction accuracy on the test data.  Four measures of prediction accuracy were used:

1. MAPE - Mean Absolute Percentage Error
2. MPE - Mean Percentage Error
3. MSE - Mean Squared Error
4. RMSE - Root Mean Squared Error

In addition, a percent accuracy measure was computed as the percentage of the observations in the test set in which the actual log number of IMDB votes fell within the prediction interval.

`r kfigr::figr(label = "prediction_comparison", prefix = TRUE, link = TRUE, type="Table")` Model Predictive Accuracy Summary
```{r prediction_comparison}
mods <- list(modelA, modelB, modelC, modelD)
accuracy <- comparePredictions(mods = mods, test = test)
knitr::kable(accuracy, digits = 3) %>%
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```
There were no significant differences in MAPE, MSE, and RMSE between the models.  The negative MPE indicated that all models were biased with over predictions. The models *with* the influence points had slightly greater prediction accuracy though the models without the outliers had higher adjusted coefficients of determination. Given the lack of justification for excluding the influential points, models Beta and Delta were ruled out. Though models Alpha and Gamma performed identically, Alpha was selected as the most parsimonious model since two predictors accounted for  `r round(sum(modelA$anova[1:2,7]) / sum(modelA$anova[,7]) * 100, 1)`% of total variation and `r round(sum(modelA$anova[1:2,7]) / sum(modelA$anova[1:6,7]) * 100, 1)`% of variation allocated to terms. 

### Model Two: Final Multiregression Model
The final prediction equation was defined as follows:
$y_i$ =
`r modelC$coefficients$estimate[1]`
+ `r round(modelC$coefficients$estimate[2], 3)`$x_1$
+ `r round(modelC$coefficients$estimate[3], 3)`$x_2$
+ `r round(modelC$coefficients$estimate[4], 3)`$x_3$
+ `r round(modelC$coefficients$estimate[5], 3)`$x_4$
+ `r round(modelC$coefficients$estimate[6], 3)`$x_5$
+ `r round(modelC$coefficients$estimate[7], 3)`$x_6$
+ `r round(modelC$coefficients$estimate[8], 3)`$x_7$
+ `r round(modelC$coefficients$estimate[9], 3)`$x_8$
+ `r round(modelC$coefficients$estimate[10], 3)`$x_9$
+ `r round(modelC$coefficients$estimate[11], 3)`$x_{10}$
+ `r round(modelC$coefficients$estimate[12], 3)`$x_{11}$
+ `r round(modelC$coefficients$estimate[13], 3)`$x_{12}$
+ `r round(modelC$coefficients$estimate[14], 3)`$x_{13}$
+ `r round(modelC$coefficients$estimate[15], 3)`$x_{14}$
+ `r round(modelC$coefficients$estimate[16], 3)`$x_{15}$
+ `r round(modelC$coefficients$estimate[17], 3)`$x_{16}$
+ $\epsilon$

where:
$x_1$ is `r modelC$coefficients$term[2]`   
$x_2$ is `r modelC$coefficients$term[3]`   
$x_3$ is `r modelC$coefficients$term[4]`   
$x_4$ is `r modelC$coefficients$term[5]`   
$x_5$ is `r modelC$coefficients$term[6]`   
$x_6$ is `r modelC$coefficients$term[7]`   
$x_7$ is `r modelC$coefficients$term[8]`   
$x_8$ is `r modelC$coefficients$term[9]`   
$x_9$ is `r modelC$coefficients$term[10]`   
$x_{10}$ is `r modelC$coefficients$term[11]`   
$x_{11}$ is `r modelC$coefficients$term[12]`   
$x_{12}$ is `r modelC$coefficients$term[13]`   
$x_{13}$ is `r modelC$coefficients$term[14]`   
$x_{14}$ is `r modelC$coefficients$term[15]`   
$x_{15}$ is `r modelC$coefficients$term[16]`   
$x_{16}$ is `r modelC$coefficients$term[17]`   


The genre, MPAA rating and month of release variables were code 0 or 1 in accordance with the genre, MPAA rating and month of release for each observation.

#### Analysis of Variance
`r kfigr::figr(label = "modelC_anova", prefix = TRUE, link = TRUE, type="Figure")` summarizes the analysis of variance.
```{r modelC_anova}
a <- modelC$anova
knitr::kable(a, digits = 3) %>%
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```
`r kfigr::figr(label = "modelC_anova", prefix = TRUE, link = TRUE, type="Figure")` Model Alpha analysis of variance

`r modelC$comments$anova`

#### Interpretation of Coefficients
Although there were *only* `r nrow(modelC$build)` variables, there were some `r nrow(modelC$coefficients)` coefficients, a consequence of the number of levels in the categorical variables. The coefficients estimates are identified in `r kfigr::figr(label = "modelC_coef", prefix = TRUE, link = TRUE, type="Table")`.

`r kfigr::figr(label = "modelC_coef", prefix = TRUE, link = TRUE, type="Table")`: Model Alpha Coefficients
```{r modelC_coef}
knitr::kable(modelC$coefficients, digits = 3) %>%
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

The intercept estimate, `r round(modelC$coefficients$estimate[1], 3)` , is the regression estimate for the mean log number of IMDB votes for a G-rated action and adventure film, with zeros for all of the other variables.  The other coefficient estimates adjust the estimate accordingly. Therefore a prediction for the log number of IMDB votes was equal to:  
* the intercept value, `r round(modelC$coefficients$estimate[1], 3)`,    
* plus `r round(subset(modelC$coefficients, term == "cast_scores", select = estimate), 3)` log IMDB votes for each point score for the cast members,  
It should be noted that the influence of cast votes and the log was not significant.

## Model Two: Simple Linear Regression
```{r modelTwo_analysis}
runmodelTwo <- function() {
  homoscedasticity <- FALSE
  out <- c()
  while(homoscedasticity == FALSE) {
    mData <- process(mdb2, stage = "a", y = "box_office_log", outliers = out)
    m <- slr(mData$full, y = "box_office_log") 
    modelTwo <- regressionAnalysis(mod = m, mName = "Model Two", yVar  = 'box_office_log',
                                 yLab = "Log Daily Box Office") 
    if (modelTwo$tests$homoscedasticity$p > .05) {
      homoscedasticity <- TRUE
      save(modelTwo, file = '../data/modelTwo.Rdata')
    } else {
      out <- c(out, modelTwo$tests$influential)
    }
  }
  return(modelTwo)
}

if (rerun == TRUE) {
  modelTwo <- runmodelTwo()
  rerun <- FALSE
} else {
  load(file = '../data/modelTwo.Rdata')
}

```

### Model Overview
A simple linear regression was calculated to predict the log of box office revenue based upon the log of the number of IMDB votes. A significant regression equation was found (F(`r modelTwo$glance$df`,`r modelTwo$glance[1,4]`) = `r round(modelTwo$glance[1,5], 3)`, p < .001), with an $R^2$ of `r round(modelTwo$glance[1,8], 3)`. The prediction equation is as follows:   

$y_i$ = `r round(modelTwo$coefficients$estimate[1], 2)` 
+ `r round(modelTwo$coefficients$estimate[2], 2)`$x_1$
+ $\epsilon$    

where:  
$x_1$ is `r modelTwo$coefficients$term[2]` 

`r kfigr::figr(label = "modelTwo_comparison", prefix = TRUE, link = TRUE, type="Table")`: Best performing simple linear regression on log of box office revenue 
```{r modelTwo_comparison}
knitr::kable(head(modelTwo$anova, 5), digits = 2) %>%
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")  
```

### Model Diagnostics
#### Linearity
The linearity of the predictor with the log of  box office is illustrated in `r kfigr::figr(label = "modelTwo_linearity", prefix = TRUE, link = TRUE, type="Figure")`.  

```{r modelTwo_linearity}
modelTwo$plots$linearity[[1]]
```
`r kfigr::figr(label = "modelTwo_linearity", prefix = TRUE, link = TRUE, type="Figure")` Model Two linearity plot

`r modelTwo$comment$linearity`

#### Homoscedasticity
The following plot (`r kfigr::figr(label = "modelTwo_homoscedasticity", prefix = TRUE, link = TRUE, type="Figure")`) of the residuals versus the fitted values provides a graphic indication of the distribution of residual variances. 
```{r modelTwo_homoscedasticity}
modelTwo$plots$res_fitted
```
`r kfigr::figr(label = "modelTwo_homoscedasticity", prefix = TRUE, link = TRUE, type="Figure")` Model Two homoscedasticity plot

`r modelTwo$comments$homoscedasticity`

#### Residuals
The histogram and the normal Q-Q plot in `r kfigr::figr(label = "modelTwo_residuals", prefix = TRUE, link = TRUE, type="Figure")` illustrate the distribution of residuals.

```{r modelTwo_residuals}
gridExtra::grid.arrange(modelTwo$plots$res_hist, modelTwo$plots$res_qq, ncol = 2)

```
`r kfigr::figr(label = "modelTwo_residuals", prefix = TRUE, link = TRUE, type="Figure")` Model Two residuals plot

`r modelTwo$comments$normality`
  
#### Outliers
```{r modelTwo_outliers}
gridExtra::grid.arrange(modelTwo$plots$res_leverage, modelTwo$plots$cooks, ncol = 2)
```
`r kfigr::figr(label = "modelTwo_outliers", prefix = TRUE, link = TRUE, type="Figure")` Model Two Outliers

`r modelTwo$comments$outliers` A case-wise review of the influential points did not reveal any data quality issues; therefore, the influential points were not removed from the model. 

## Model Summary
The purpose of this section was to develop models that would predict "box office success". Therefore, two regression models were fit in this section: Model One (F(`r modelC$glance[1,3]`, `r modelC$glance[1,4]`) = `r round(modelC$glance[1,5], 2)`, p < .001) was selected from among four multiregression linear models employing forward selection and backward elimination algorithms. Model Two, a simple linear regression model (F(`r modelTwo$glance[1,3]`, `r modelTwo$glance[1,4]`) = `r round(modelTwo$glance[1,5],2)`, p < .001) predicts log box office revenue based upon the log IMDB votes.

Next, the models will be used to predict the number of log IMDB votes and the log box office for a randomly selected film.


* * *
