# Part 7: Conclusion
```{r conclusion}
conclusions <- conclusion(slr = modelTwo, mlr = modelA, data = train)

genrePlots <- conclusions$genre$plots
castPlots <- conclusions$cast$plots
runtimePlots <- conclusions$runtime$plots

genreData <- conclusions$genre$data %>% arrange(desc(pctChgRevenue))
castData <- conclusions$cast$data %>% arrange(desc(pctChgRevenue))
runtimeData <- conclusions$runtime$data %>% arrange(desc(pctChgRevenue))


```

The purpose of this analysis was to determine the factors that make a movie popular, in terms of box office success. More to the point, the aim was to generate insight that would inform the decisions studio executives must make at project inception or in the early stages of a film project. That said, features of interest were those that were *knowable* by studio executives at or near project outset. As such, variables such as critics scores/ratings, audience scores/ratings, IMDB rating, academy awards, and box office success, were only considered as possible dependent variables to predict, but not as independent variables. Instead, new features that characterized actor and director experience and popularity from a historical point of view, were created. 

To relate the available data to box office revenue, box office figures were obtained for approximately 250 random samples from the original data and correlation tests indicated that the log of IMDB votes was the most highly correlated variable with the log of box office revenue. Two regression models were trained: (1) a multiple regression model which predicted the log of IMDB votes, based upon available and derived data as described above, and (2) a simple linear regression model which predicted the log of box office revenue based upon the predicted log IMDB votes. Based upon this analysis and the available data, three key observations emerged as noteworthy.

## Cast 
Casting is certainly one of the most important decisions a studio executive or casting director must make and the selection process, one would suspect, is quite complex with a variety of factors influencing the decision.  This analysis has revealed the box office value of empirically determining actor popularity, based upon ratings such as those provided by IMDB and Rottentomatoes, and using that information to maximize *total* cast popularity, given other considerations. For this analysis, actor popularity was derived from a composite total score for a film, equal to 10 x the IMDB rating plus the audience score.  For each film, the total film score was apportioned among the five credited actors as follows:  
* Actor 1: 40%  
* Actor 2: 30%  
* Actor 3: 15%  
* Actor 4: 10%  
* Actor 5: 5%  

Scores were computed for each actor and the cast score was the sum of the actor scores for that film. This measure accounted for `r round(modelA$anova %>% filter(Term == 'cast_scores') %>% select(7), 2)`% of total variance and  `r round(modelA$anova %>% filter(Term == 'cast_scores') %>% select(7) / sum(modelA$anova[1:(nrow(modelA$anova)-1),7]) * 100, 2)`% of the variance attributed to the terms. 

`r kfigr::figr(label = "cast", prefix = TRUE, link = TRUE, type="Figure")` illustrates the effect of cast scores on IMDB votes, and  box office revenue. 

```{r cast, fig.height=10}
library(gridExtra)
n <- length(castPlots)
nCol <- floor(sqrt(n))
do.call("grid.arrange", c(castPlots, ncol=nCol))
```
`r kfigr::figr(label = "cast", prefix = TRUE, link = TRUE, type="Figure")`: Impact of cast scores on box office 

As shown in the top two charts in `r kfigr::figr(label = "cast", prefix = TRUE, link = TRUE, type="Figure")`, the logs of IMDB votes and box office grow linearly with cast scores; but they have an accelerated effect on IMDB votes and box office revenue on the linear scale. A one percent change in cast scores results in a `r round(exp(modelA$coefficients[12,2] - 1) * 100, 0)`% change in IMDB votes and a `r round(max(castData$pctChgRevenue) / max(castData$pctChgScore) * 100`% change in box office revenue. Introducing such analytics to the casting process could result in significant gains at the box office.


## Genre
The multiregression analysis showed that genre accounts for `r round(modelA$anova %>% filter(Term == 'genre') %>% select(7), 2)`% of total variance and  `r round(modelA$anova %>% filter(Term == 'genre') %>% select(7) / sum(modelA$anova[1:(nrow(modelA$anova)-1),7]) * 100, 2)`% of the variance attributed to the terms. `r kfigr::figr(label = "genres", prefix = TRUE, link = TRUE, type="Figure")` illuminates the effect of genre on IMDB votes and box office revenue.  

```{r genres, fig.height=10}
library(gridExtra)
n <- length(genrePlots)
nCol <- floor(sqrt(n))
do.call("grid.arrange", c(genrePlots, ncol=nCol))
```
`r kfigr::figr(label = "genres", prefix = TRUE, link = TRUE, type="Figure")`: Genre Analysis

Science fiction fantasy, action & adventure, and horror are the top three box office earners according to this analysis.  Using comedy as the reference level, science fiction and fantasy earns `r round(genreData$pctChgVotes[1], 0)`% more IMDB votes than comedy and `r round(genreData$pctChgRevenue[1], 0)`% more revenue, all other factors constant. Action and adventure receives `r round(genreData$pctChgVotes[2], 0)`%  and `r round(genreData$pctChgRevenue[2], 0)`% more IMDB votes and box office revenue than comedy, respectively. Similarly, horrors produce `r round(genreData$pctChgVotes[3], 0)`%  and `r round(genreData$pctChgRevenue[3], 0)`%  more IMDB votes and box office revenue than comedy, respectively. So sayeth, the numbers.

## Runtime
Runtime, or its log transformation accounting for just `r modelA$anova[modelA$anova$Term == "runtime_log", 7]`% of the variance in the model, repeatedly emerged as a signficant predictor of IMDB votes. In fact, relative to the other factors its impact was substantial. A one percent change in runtime resulted in a  `r round(exp(modelA$coefficients[13,2] - 1) * 100, 0)`% change in the number of IMDB votes and a `r round(max(runtimeData$pctChgRevenue) / max(runtimeData$pctChgRuntime), 0)`% change in revenue.

```{r runtime, fig.height=10}
library(gridExtra)
n <- length(runtimePlots)
nCol <- floor(sqrt(n))
do.call("grid.arrange", c(runtimePlots, ncol=nCol))
```
`r kfigr::figr(label = "runtime", prefix = TRUE, link = TRUE, type="Figure")`: Impact of runtime on box office 

What emerged is that runtime was likely a proxy for a variety of hidden factors such as production budget. High budget films tend to attract the best producers, directors, actors and crew. So, runtime is less a predictor of box office success, but an indicator. 

## Future Study
Future studies would benefit from significantly more depth and breadth of data. An adequate volume of data would refine predictions vis-a-vis actor / director experience and popularity.  Expanding the feature set to include production budget, genre vis-a-vis demographic data, historical box office revenue, social media information, and topic data would provide for a more sophisticated model with greater generalizability. 


* * *
