# Part 7: Conclusion
```{r conclusion}
conclusions <- conclusion(slr = modelOne, mlr = modelA, data = train)
```

The purpose of this analysis was to determine the factors that make a movie popular, in terms of box office revenue. Concretely, the focus was on the decisions a studio executive can make at the inception of a film project to maximize box office revenue. Though the data contained *measures* of popularity, such as audience ratings, critics scores, top 200 box office and academy award success, there was a dearth of information available with which to predict success. Focusing only on those variables that are "knowable" at project inception, the analysis was limited to the following possible predictors:  

`r kfigr::figr(label = "predictors", prefix = TRUE, link = TRUE, type="Table")`: Multiregression prediction variables
```{r predictors}
features <- openxlsx::read.xlsx(xlsxFile = "../data/features.xlsx")
features <- features %>% filter(c == "yes") %>% select(Variable, Description) %>% arrange(Variable)
knitr::kable(features, digits = 2) %>%
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

The available data suggest that the two most important decisions a studio executive can make at project inception to maximize box office revenue is the selection of cast and genre.

## Cast 
Cast votes is a measure of the popularity of actors, and account for `r round(modelA$anova %>% filter(Term == 'cast_scores') %>% select(7), 2)`% of total variance and  `r round(modelA$anova %>% filter(Term == 'cast_scores') %>% select(7) / sum(modelA$anova[1:6,7]) * 100, 2)`% of the variance attributed to the terms. Measured as the sum of the total number of point scores allocated to each cast member from prior work; whereby, the total cast score for a film, calculated as 10 x the IMDB rating plus the audience score, was apportioned to the actors as follows:   
* Actor 1: 40%  
* Actor 2: 30%  
* Actor 3: 15%  
* Actor 4: 10%   
* Actor 5: 5%  

`r kfigr::figr(label = "castVotes", prefix = TRUE, link = TRUE, type="Table")`: Cast Votes Analysis
```{r castVotes}
knitr::kable(conclusions$castScores, digits = 3) %>%
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

`r kfigr::figr(label = "castVotes", prefix = TRUE, link = TRUE, type="Table")` shows the effect of cast scores at various points in the sample data. Casting actors with high scores can dramatically affect potential box office revenue. A `r round(conclusions$castScores[2,6] / conclusions$castScores[5,6], 0) -1` fold increase in cast scores produces an equivalent increase in estimated daily box office revenue. However, a `r round(conclusions$castScores[1,6] / conclusions$castScores[5,6], 0) -1` increase in cast scores could produce upwards of a `r round(conclusions$castScores[1,5] / conclusions$castScores[5,5], 0) -1` increase daily at the box office. Cast is likely the single most important decision a studio executive can make at project inception.

## Genre
The multiregression analysis showed that genre accounts for `r round(modelA$anova %>% filter(Term == 'genre') %>% select(7), 2)`% of total variance and  `r round(modelA$anova %>% filter(Term == 'genre') %>% select(7) / sum(modelA$anova[1:6,7]) * 100, 2)`% of the variance attributed to the terms. `r kfigr::figr(label = "genres", prefix = TRUE, link = TRUE, type="Table")` shows the estimates for the slope, log IMDB votes, log daily box office, and % increase in box office revenue on the linear scale for films with zeros for the other variables in the regression. 

`r kfigr::figr(label = "genres", prefix = TRUE, link = TRUE, type="Table")`: Genre Analysis
```{r genres}
knitr::kable(conclusions$genres, digits = 3) %>%
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

In order of influence, action and adventure films are the most popular, followed by science fiction & fantasy and horror. Considering documentaries as a baseline, the revenue for action and adventure, science fiction, and horror films would be `r round(genres[1,5] / genres[nrow(genres),5], -1)`, `r round(genres[2,5] / genres[nrow(genres),5], -1)` and `r round(genres[3,5] / genres[nrow(genres),5], -1)` fold increase in box office revenue over documentaries, respectively. 



* * *
