# Appendix
## Appendix A: Source Code
This appendix includes the primary functions used to perform forward selection, backward elimination, and prediction. The rest of the source code is available on github at https://github.com/DataScienceSalon/mdb.

### Forward Selection
This function performs the forward selection process.
```{r a-forward, code=readLines('../R/forward.R')[24:100], echo=TRUE, eval=FALSE}
```

### Backward Elimination
This function performs backward elimination.
```{r a-backward, code=readLines('../R/back.R')[18:82], echo=TRUE, eval=FALSE}
```

### Regression Analysis
The regression analysis function performs the tests, and renders the plots requuired to validate the regression assumptions.
```{r a-prediction, code=readLines('../R/regressionAnalysis.R')[19:285], echo=TRUE, eval=FALSE}
```

### Prediction    
This function performs the prediction of the ten test films   
```{r a-prediction, code=readLines('../R/prediction.R')[20:57], echo=TRUE, eval=FALSE}
```

## Appendix B: Formulas
The cast scores and cast votes variables characterized the overall popularity of the cast. Total scores, defined as 10 * IMDb rating plus the audience score, was apportioned according to proportional allocation and this value was summed over the individual cast members.  The cast score variable was derived as follows:   
$$cs_i = [\displaystyle\sum_{a=1}^5 \displaystyle\sum_{f_a=1}^n s_{f_a} * p_a] - s_i $$
where:  
$cs_i$ is the cast score for film $i$  
$a$ is the variable containing the five credited actors   
$f_a$ is the film in which actor was credited  
$n$ is the number of films in which the actor was credited  
$s_{f_a}$ is the total score for film $f_a$, computed as (10 * imdb_rating) + audience score  
$p_a$ is the proportion of $s_{f_a}$ allocated to actor $a$ and is defined as:   
Actor 1: .40 * $s_{f_a}$  
Actor 1: .30 * $s_{f_a}$  
Actor 1: .15 * $s_{f_a}$  
Actor 1: .10 * $s_{f_a}$  
Actor 1: .05 * $s_{f_a}$  
$s_i$ is the total score for film $i$

The cast votes variable was computed analogously.
