---
title: "Movie Rating Model and Predictor"
author: "John James jjames@datasciencesalon.org"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  rmdformats::readthedown:
    highlight: kate
    css: rmdStyles.css
bibliography: library.bib
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r knitr_init, echo=FALSE, cache=FALSE, warning=FALSE, message=FALSE}
options(knitr.table.format = "html")
options(max.print=100, scipen=999, width = 800)
knitr::opts_chunk$set(echo=FALSE,
	             cache=FALSE,
               prompt=FALSE,
	             eval = TRUE,
               tidy=TRUE,
               root.dir = "..",
               fig.height = 8,
               fig.width = 20,
               comment=NA,
               message=FALSE,
               warning=FALSE)
knitr::opts_knit$set(width=100, figr.prefix = T, figr.link = T)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=",")
})
```

```{r load-data}
#mdb2 <- openxlsx::read.xlsx("../data/sample.xlsx")
#save(file = "../data/mdb2.RData", mdb2)
load("../data/movies.Rdata")
load("../data/mdb2.Rdata")
```

```{r load-libraries}
library(dplyr)
library(extrafont)
library(ggplot2)
```

```{r source-functions}
source("../R/analysis.R")
source("../R/associate.R")
source("../R/back.R")
source("../R/bivariate.R")
source("../R/correlate.R")
source("../R/forward.R")
source("../R/fullModel.R")
source("../R/preprocess.R")
source("../R/process.R")
source("../R/regressionAnalysis.R")
source("../R/univariate.R")
source("../R/univariateQual.R")
source("../R/univariateQuant.R")
source("../R/visualization.R")
```


```{r mdb}
dataSets  <- preprocess(movies, mdb2)
mdb <- dataSets$mdb1
mdb2 <- dataSets$mdb2
edaUni <- univariate(mdb)
```

# Part 1: Data
The data were comprised of audience and critics opinions, awards, studio, and actor information from Rotten Tomatoes, imdb, and BoxOfficeMojo.com for a random sample of 651 movies produced and released prior to 2016. 

## Data Sources
### Rotten Tomatoes
Launched in August 1998 by Senh Duong, Rotten Tomatoes is an American review aggregation website for film and television. 

### IMDB

## Generalizability

## Data Preprocessing
As a first step, variables such as website addresses and film titles were removed from the data set, then some 619 completed cases were extracted for downstream analysis. Since the focus was on theatrical releases, TV movies were excised from the data set. Next, three additional data sets were created:  
* Film Box Office
* Director Profiles  
* Actor Profiles

**Film Box Office**
The overarching aim was to understand which factors most influenced box office success for a film. Since box office revenue was not among the features provided in the data set, the first preprocessing step was to identify (or create) a response variable that would correlate with box office success. As such, total box office was obtained from the BoxOfficeMojo.com site for a random sampling of some `r round(nrow(mdb2), -1)` films from the original sample. The first step in the bivariate analysis was to identify which of the provided variables (or variables derived from those provided) most correlated with box office success.

**Director / Actor Profiles:** 
The purpose of the director/actor profiles was to capture the experience and popularity of each director and actor. The experience variables were simply the total number of films in the sample in which the director or actor was listed in the original sample.  Popularity, in the director's case was the sum of the IMDB votes for the director's films.  Similarly, the popularity for an actor was the sum of the *allocated* IMDB votes for films in which the actor was listed as one of the top 5. Actors were allocated IMDB votes as follows:   
* 40% of total film IMDB votes for actor1    
* 30% of total film IMDB votes for actor2   
* 15% of total film IMDB votes for actor3  
* 10% of total film IMDB votes for actor4  
* 5% of total film IMDB votes for actor5  
These variables were then merged into the main sample data set.

**Variables Added**
A variable was created to capture the number of days between theatrical and dvd release. A composite score variable defined as 10 * IMDB Rating + critics score + audience_score was created and lastly, log transformations were applied to certain variables such as IMDB and cast votes. To sum, the following variables listed in `r kfigr::figr(label = "derived", prefix = TRUE, link = TRUE, type="Table")` were added to the data set.  
`r kfigr::figr(label = "derived", prefix = TRUE, link = TRUE, type="Table")`: Variables added to the data set
```{r derived}
raw <- openxlsx::read.xlsx(xlsxFile = "../data/features.xlsx")
derived <- raw %>% filter(Source == "Derived") %>% select(Variable, Description) %>% arrange(Variable)
knitr::kable(derived) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

**Variables Removed**
The following variables listed in `r kfigr::figr(label = "removed", prefix = TRUE, link = TRUE, type="Table")` were removed from the data set for the reasons listed below.  
`r kfigr::figr(label = "removed", prefix = TRUE, link = TRUE, type="Table")`: Variables removed from the data set
```{r removed}
raw <- openxlsx::read.xlsx(xlsxFile = "../data/features.xlsx")
removed <- raw %>% filter(uni == "no") %>% select(Variable, Description, Rationale) %>% arrange(Variable)
knitr::kable(removed) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

The full resultant codebook for the data set can be found in Appendix A

* * *

# Part 2: Research question
The underlying intent of this analysis was to determine the factors that most influence box office success for a film. Since box office revenue was not among the variables included in the raw data set, the first task was to determine which of the selected (or derived) variables would stand as a proxy for box office success. As such the first research question is concretely stated as follows:  
> Which of the selected or derived variables is most highly associated / correlated with total lifetime box office revenue  

Once this proxy response variable was determined, the features that are most highly associated / correlated with this response variable were examined via the following research question.  
> Which features are most highly associated / correlated with the proxy response for box office success

* * *

# Part 3: Exploratory data analysis
The exploratory data analysis comprised both a univariate and bivariate examination of the variables. 

## Univariate Analysis
### Univariate Analysis of Categorical Variables
The purpose of the univariate analysis of categorical variables was to examine the relative frequencies and proportions of observations for each level of the categorical level.  The categorical variables included at this stage of the analysis are indicated in `r kfigr::figr(label = "uni_cat", prefix = TRUE, link = TRUE, type="Table")`.  

`r kfigr::figr(label = "uni_cat", prefix = TRUE, link = TRUE, type="Table")`: Categorical Variables
```{r uni_cat}
raw <- openxlsx::read.xlsx(xlsxFile = "../data/features.xlsx")
uniCat <- raw %>% filter(uni == "yes" & Type == "Categorical") %>% select(Variable, Description) %>% arrange(Variable)
knitr::kable(uniCat) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

For brevity reasons, this section briefly covers the five variables most important to the modeling effort, in priority order. The complete analysis can be found in Appendix B. 

#### Director
The work of `r length(unique(mdb$director))` directors was included in the sample provided for this project. Data with respect to the number of films in the sample per director were captured in the director experience variable defined in the quantitative section.

#### Genre
The drama genre represented a plurality of the releases in the sample, followed by comedy action & adventure then mystery & suspense. The top four genres account for nearly `r round(sum(head(edaUni$genre$stats %>% arrange(desc(Proportion)) %>% select(Proportion), 4)) * 100, -1)`% of the films in the sample. 
```{r genre}
edaUni$genre$plot
```
`r kfigr::figr(label = "genre", prefix = TRUE, link = TRUE, type="Figure")`: Films by genre

#### MPAA Rating
Rated R films accounted for over `r round(edaUni$mpaa$stats$Proportion[5] * 100, -1)`% of the releases, followed by PG and PG-13. Collectively, R, PG, and PG-13 rated films represent `r round(sum(head(edaUni$mpaa$stats %>% arrange(desc(Proportion)) %>% select(Proportion), 3)) * 100, -1)`% of the films in the sample. NC-17 films were excluded from this analysis.
```{r mpaa}
edaUni$mpaa$plot
```
`r kfigr::figr(label = "mpaa", prefix = TRUE, link = TRUE, type="Figure")`: Films by MPAA Rating

#### Best Picture 
The best picture nomination variable proved to be among the top five most influential categorical variables.
```{r a_best_picture}
gridExtra::grid.arrange(edaUni$bestPicNom$plot, edaUni$bestPicWin$plot, ncol = 2)
```
`r kfigr::figr(label = "a_best_picture", prefix = TRUE, link = TRUE, type="Figure")`: Best picture nominations and wins

#### Month of Theatrical Release
The plurality of features in the sample (`r sum(edaUni$month$stats$Proportion[c(1,6,10,12)])*100`%) were released during the months of January, June, October and December.  
```{r month}
edaUni$month$plot
```
`r kfigr::figr(label = "month", prefix = TRUE, link = TRUE, type="Figure")`: Theatrical releases by month


### Univariate Analysis of Quantitative Variables
The primary aim of this analysis was to examine the distribution of the variables vis-a-vis a normal distribution, and to identify potential outliers.  Summary statistics, histograms, boxplots, normal quantile-quantile plots were rendered for each variable. The quantitative variables included at this stage of the analysis are indicated in `r kfigr::figr(label = "uni_quant", prefix = TRUE, link = TRUE, type="Table")`.

`r kfigr::figr(label = "uni_quant", prefix = TRUE, link = TRUE, type="Table")`: Quantitative Variables
```{r uni_quant}
uniQuant <- raw %>% filter(uni == "yes" & Type == "Numeric") %>% select(Variable, Description)
knitr::kable(uniQuant) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

Again, the five most influential quantitative variables are covered here in some detail. The complete analysis can be found in Appendix B.

#### Director Experience
This derived variable measured the relative experience of a given director and was defined as the sum of the observations for the director associated with each film.  

`r kfigr::figr(label = "director_experience_stats", prefix = TRUE, link = TRUE, type="Table")`: Director experience summary statistics
```{r director_experience_stats}
knitr::kable(edaUni$directorExperience$stats, digits = 2) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

```{r director_experience_dist}
gridExtra::grid.arrange(edaUni$directorExperience$hist, edaUni$directorExperience$qq, ncol = 2)
```
`r kfigr::figr(label = "director_experience_dist", prefix = TRUE, link = TRUE, type="Figure")`: Director experience histogram and QQ Plot

```{r director_experience_box, fig.height=4}
edaUni$directorExperience$box
```
`r kfigr::figr(label = "director_experience_box", prefix = TRUE, link = TRUE, type="Figure")`: Director experience boxplot

**Central Tendency**: The summary statistics (`r kfigr::figr(label = "director_experience_stats", prefix = TRUE, link = TRUE, type="Table")`) `r edaUni$directorExperience$central`

**Dispersion**: `r edaUni$directorExperience$disp`

**Shape of Distribution**:  `r edaUni$directorExperience$skew` `r edaUni$directorExperience$kurt` The histogram and QQ plot in `r kfigr::figr(label = "director_experience_dist", prefix = TRUE, link = TRUE, type="Figure")` reveal a distribution which departs significantly from normality.

**Outliers**: The boxplot in `r kfigr::figr(label = "director_experience_box", prefix = TRUE, link = TRUE, type="Figure")`, which graphically depicts the median, the IQR, and maximum and minimum values, suggested that `r ifelse(nrow(edaUni$directorExperience$outliers) == 0, "no", " ")` outliers were extant. `r edaUni$directorExperience$out` Given the proximity of the outliers to the 1.5xIQR, no effort was made to remove them.

#### Cast Experience
This derived variable measured the relative experience of a given cast and was defined as the sum of the observations for the cast associated with each film.  

`r kfigr::figr(label = "cast_experience_stats", prefix = TRUE, link = TRUE, type="Table")`: Cast experience summary statistics
```{r cast_experience_stats}
knitr::kable(edaUni$castExperience$stats, digits = 2) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

```{r cast_experience_dist}
gridExtra::grid.arrange(edaUni$castExperience$hist, edaUni$castExperience$qq, ncol = 2)
```
`r kfigr::figr(label = "cast_experience_dist", prefix = TRUE, link = TRUE, type="Figure")`: Cast experience histogram and QQ Plot

```{r cast_experience_box, fig.height=4}
edaUni$castExperience$box
```
`r kfigr::figr(label = "cast_experience_box", prefix = TRUE, link = TRUE, type="Figure")`: Cast experience boxplot

**Central Tendency**: The summary statistics (`r kfigr::figr(label = "cast_experience_stats", prefix = TRUE, link = TRUE, type="Table")`) `r edaUni$castExperience$central`

**Dispersion**: `r edaUni$castExperience$disp`

**Shape of Distribution**:  `r edaUni$castExperience$skew` `r edaUni$castExperience$kurt` The histogram and QQ plot in `r kfigr::figr(label = "cast_experience_dist", prefix = TRUE, link = TRUE, type="Figure")` reveal a distribution which departs significantly from normality.

**Outliers**: The boxplot in `r kfigr::figr(label = "cast_experience_box", prefix = TRUE, link = TRUE, type="Figure")`, which graphically depicts the median, the IQR, and maximum and minimum values, suggested that `r ifelse(nrow(edaUni$castExperience$outliers) == 0, "no", " ")` outliers were extant. `r edaUni$castExperience$out` Given the proximity of the outliers to the 1.5xIQR, no effort was made to remove them.

#### Number of IMDB Votes 
This variable captured the number of IMDB votes cast for each film.

`r kfigr::figr(label = "imdb_votes_stats", prefix = TRUE, link = TRUE, type="Table")`: IMDB votes summary statistics
```{r imdb_votes_stats}
knitr::kable(edaUni$imdbVotes$stats, digits = 2) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

```{r imdb_votes_dist}
gridExtra::grid.arrange(edaUni$imdbVotes$hist, edaUni$imdbVotes$qq, ncol = 2)
```
`r kfigr::figr(label = "imdb_votes_dist", prefix = TRUE, link = TRUE, type="Figure")`: IMDB votes histogram and QQ Plot

```{r imdb_votes_box, fig.height=4}
edaUni$imdbVotes$box
```
`r kfigr::figr(label = "imdb_votes_box", prefix = TRUE, link = TRUE, type="Figure")`: IMDB votes boxplot

**Central Tendency**: The summary statistics (`r kfigr::figr(label = "imdb_votes_stats", prefix = TRUE, link = TRUE, type="Table")`) `r edaUni$imdbVotes$central`

**Dispersion**: `r edaUni$imdbVotes$disp`

**Shape of Distribution**:  `r edaUni$imdbVotes$skew` `r edaUni$imdbVotes$kurt` The histogram and QQ plot in `r kfigr::figr(label = "imdb_votes_dist", prefix = TRUE, link = TRUE, type="Figure")` reveal a distribution which departs significantly from normality.

**Outliers**: The boxplot in `r kfigr::figr(label = "imdb_votes_box", prefix = TRUE, link = TRUE, type="Figure")`, which graphically depicts the median, the IQR, and maximum and minimum values, suggested that `r ifelse(nrow(edaUni$imdbVotes$outliers) == 0, "no", " ")` outliers were extant. `r edaUni$imdbVotes$out` 

#### Log Number of IMDB Votes 
This was a log transformation of the IMDB votes variable.

`r kfigr::figr(label = "imdb_votes_log_stats", prefix = TRUE, link = TRUE, type="Table")`: Log IMDB votes summary statistics
```{r imdb_votes_log_stats}
knitr::kable(edaUni$imdbVotesLog$stats, digits = 2) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

```{r imdb_votes_log_dist}
gridExtra::grid.arrange(edaUni$imdbVotesLog$hist, edaUni$imdbVotesLog$qq, ncol = 2)
```
`r kfigr::figr(label = "imdb_votes_log_dist", prefix = TRUE, link = TRUE, type="Figure")`: Log IMDB votes histogram and QQ Plot

```{r imdb_votes_log_box, fig.height=4}
edaUni$imdbVotesLog$box
```
`r kfigr::figr(label = "imdb_votes_log_box", prefix = TRUE, link = TRUE, type="Figure")`: Log IMDB votes boxplot

**Central Tendency**: The summary statistics (`r kfigr::figr(label = "imdb_votes_log_stats", prefix = TRUE, link = TRUE, type="Table")`) `r edaUni$imdbVotesLog$central`

**Dispersion**: `r edaUni$imdbVotesLog$disp`

**Shape of Distribution**:  `r edaUni$imdbVotesLog$skew` `r edaUni$imdbVotesLog$kurt` The histogram and QQ plot in `r kfigr::figr(label = "imdb_votes_log_dist", prefix = TRUE, link = TRUE, type="Figure")` reveal a nearly normal distribution.

**Outliers**: The boxplot in `r kfigr::figr(label = "imdb_votes_log_box", prefix = TRUE, link = TRUE, type="Figure")`, which graphically depicts the median, the IQR, and maximum and minimum values, suggested that `r ifelse(nrow(edaUni$imdbVotesLog$outliers) == 0, "no", " ")` outliers were extant. `r edaUni$imdbVotesLog$out` 

#### IMDB Ratings
This variable captured the IMDB rating for each film

`r kfigr::figr(label = "imdb_rating_stats", prefix = TRUE, link = TRUE, type="Table")`: IMDB rating summary statistics
```{r imdb_rating_stats}
knitr::kable(edaUni$imdbRating$stats, digits = 2) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

```{r imdb_rating_dist}
gridExtra::grid.arrange(edaUni$imdbRating$hist, edaUni$imdbRating$qq, ncol = 2)
```
`r kfigr::figr(label = "imdb_rating_dist", prefix = TRUE, link = TRUE, type="Figure")`: IMDB rating histogram and QQ Plot

```{r imdb_rating_box, fig.height=4}
edaUni$imdbRating$box
```
`r kfigr::figr(label = "imdb_rating_box", prefix = TRUE, link = TRUE, type="Figure")`: IMDB rating boxplot

**Central Tendency**: The summary statistics (`r kfigr::figr(label = "imdb_rating_stats", prefix = TRUE, link = TRUE, type="Table")`) `r edaUni$imdbRating$central`

**Dispersion**: `r edaUni$imdbRating$disp`

**Shape of Distribution**:  `r edaUni$imdbRating$skew` `r edaUni$imdbRating$kurt` The histogram and QQ plot in `r kfigr::figr(label = "imdb_rating_dist", prefix = TRUE, link = TRUE, type="Figure")` reveal a nearly normal distribution.

**Outliers**: The boxplot in `r kfigr::figr(label = "imdb_rating_box", prefix = TRUE, link = TRUE, type="Figure")`, which graphically depicts the median, the IQR, and maximum and minimum values, suggested that `r ifelse(nrow(edaUni$imdbRating$outliers) == 0, "no", " ")` outliers were extant. `r edaUni$imdbRating$out` 

#### Critics Scores
This variable captured the critics scores for each film

`r kfigr::figr(label = "critics_scores_stats", prefix = TRUE, link = TRUE, type="Table")`: Critics score summary statistics
```{r critics_scores_stats}
knitr::kable(edaUni$criticsScores$stats, digits = 2) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

```{r critics_scores_dist}
gridExtra::grid.arrange(edaUni$criticsScores$hist, edaUni$criticsScores$qq, ncol = 2)
```
`r kfigr::figr(label = "critics_scores_dist", prefix = TRUE, link = TRUE, type="Figure")`: Critics score histogram and QQ Plot

```{r critics_scores_box, fig.height=4}
edaUni$criticsScores$box
```
`r kfigr::figr(label = "critics_scores_box", prefix = TRUE, link = TRUE, type="Figure")`: Critics score boxplot

**Central Tendency**: The summary statistics (`r kfigr::figr(label = "critics_scores_stats", prefix = TRUE, link = TRUE, type="Table")`) `r edaUni$criticsScores$central`

**Dispersion**: `r edaUni$criticsScores$disp`

**Shape of Distribution**:  `r edaUni$criticsScores$skew` `r edaUni$criticsScores$kurt` The histogram and QQ plot in `r kfigr::figr(label = "critics_scores_dist", prefix = TRUE, link = TRUE, type="Figure")` reveals a left skewed distribution that departs from normality.  

**Outliers**: The boxplot in `r kfigr::figr(label = "critics_scores_box", prefix = TRUE, link = TRUE, type="Figure")`, which graphically depicts the median, the IQR, and maximum and minimum values, suggested that `r ifelse(nrow(edaUni$criticsScores$outliers) == 0, "no", " ")` outliers were extant. `r edaUni$criticsScores$out` 

#### Audience Scores
This variable captured the audience scores for each film

`r kfigr::figr(label = "audience_scores_stats", prefix = TRUE, link = TRUE, type="Table")`: Audience score summary statistics
```{r audience_scores_stats}
knitr::kable(edaUni$audienceScores$stats, digits = 2) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

```{r audience_scores_dist}
gridExtra::grid.arrange(edaUni$audienceScores$hist, edaUni$audienceScores$qq, ncol = 2)
```
`r kfigr::figr(label = "audience_scores_dist", prefix = TRUE, link = TRUE, type="Figure")`: Audience score histogram and QQ Plot

```{r audience_scores_box, fig.height=4}
edaUni$audienceScores$box
```
`r kfigr::figr(label = "audience_scores_box", prefix = TRUE, link = TRUE, type="Figure")`: Audience score boxplot

**Central Tendency**: The summary statistics (`r kfigr::figr(label = "audience_scores_stats", prefix = TRUE, link = TRUE, type="Table")`) `r edaUni$audienceScores$central`

**Dispersion**: `r edaUni$audienceScores$disp`

**Shape of Distribution**:  `r edaUni$audienceScores$skew` `r edaUni$audienceScores$kurt` The histogram and QQ plot in `r kfigr::figr(label = "audience_scores_dist", prefix = TRUE, link = TRUE, type="Figure")` reveals a left skewed distribution that departs from normality.  

**Outliers**: The boxplot in `r kfigr::figr(label = "audience_scores_box", prefix = TRUE, link = TRUE, type="Figure")`, which graphically depicts the median, the IQR, and maximum and minimum values, suggested that `r ifelse(nrow(edaUni$audienceScores$outliers) == 0, "no", " ")` outliers were extant. `r edaUni$audienceScores$out` 

#### Cast Votes
This variable captured the total number of votes allocated to each cast member for a film. 

`r kfigr::figr(label = "cast_votes_stats", prefix = TRUE, link = TRUE, type="Table")`: Cast votes summary statistics
```{r cast_votes_stats}
knitr::kable(edaUni$castVotes$stats, digits = 2) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

```{r cast_votes_dist}
gridExtra::grid.arrange(edaUni$castVotes$hist, edaUni$castVotes$qq, ncol = 2)
```
`r kfigr::figr(label = "cast_votes_dist", prefix = TRUE, link = TRUE, type="Figure")`: Cast votes histogram and QQ Plot

```{r cast_votes_box, fig.height=4}
edaUni$castVotes$box
```
`r kfigr::figr(label = "cast_votes_box", prefix = TRUE, link = TRUE, type="Figure")`: Cast votes boxplot

**Central Tendency**: The summary statistics (`r kfigr::figr(label = "cast_votes_stats", prefix = TRUE, link = TRUE, type="Table")`) `r edaUni$castVotes$central`

**Dispersion**: `r edaUni$castVotes$disp`

**Shape of Distribution**:  `r edaUni$castVotes$skew` `r edaUni$castVotes$kurt` The histogram and QQ plot in `r kfigr::figr(label = "cast_votes_dist", prefix = TRUE, link = TRUE, type="Figure")` reveals a left skewed distribution that departs significantly from normality.  

**Outliers**: The boxplot in `r kfigr::figr(label = "cast_votes_box", prefix = TRUE, link = TRUE, type="Figure")`, which graphically depicts the median, the IQR, and maximum and minimum values, suggested that `r ifelse(nrow(edaUni$castVotes$outliers) == 0, "no", " ")` outliers were extant. `r edaUni$castVotes$out` 

#### Log Cast Votes
This is a log transformation of the cast votes variable.

`r kfigr::figr(label = "cast_votes_log_stats", prefix = TRUE, link = TRUE, type="Table")`: Log cast votes summary statistics
```{r cast_votes_log_stats}
knitr::kable(edaUni$castVotesLog$stats, digits = 2) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

```{r cast_votes_log_dist}
gridExtra::grid.arrange(edaUni$castVotesLog$hist, edaUni$castVotesLog$qq, ncol = 2)
```
`r kfigr::figr(label = "cast_votes_log_dist", prefix = TRUE, link = TRUE, type="Figure")`: Log cast votes histogram and QQ Plot

```{r cast_votes_log_box, fig.height=4}
edaUni$castVotesLog$box
```
`r kfigr::figr(label = "cast_votes_log_box", prefix = TRUE, link = TRUE, type="Figure")`: Log cast votes boxplot

**Central Tendency**: The summary statistics (`r kfigr::figr(label = "cast_votes_log_stats", prefix = TRUE, link = TRUE, type="Table")`) `r edaUni$castVotesLog$central`

**Dispersion**: `r edaUni$castVotesLog$disp`

**Shape of Distribution**:  `r edaUni$castVotesLog$skew` `r edaUni$castVotesLog$kurt` The histogram and QQ plot in `r kfigr::figr(label = "cast_votes_log_dist", prefix = TRUE, link = TRUE, type="Figure")` reveals a left skewed distribution that approximates normality.  

**Outliers**: The boxplot in `r kfigr::figr(label = "cast_votes_log_box", prefix = TRUE, link = TRUE, type="Figure")`, which graphically depicts the median, the IQR, and maximum and minimum values, suggested that `r ifelse(nrow(edaUni$castVotesLog$outliers) == 0, "no", " ")` outliers were extant. `r edaUni$castVotesLog$out` 


#### Scores
This variable captured the total score for each film defined as 10 * IMDB Rating + critics score + audience_score.

`r kfigr::figr(label = "scores_stats", prefix = TRUE, link = TRUE, type="Table")`: Scores summary statistics
```{r scores_stats}
knitr::kable(edaUni$scores$stats, digits = 2) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

```{r scores_dist}
gridExtra::grid.arrange(edaUni$scores$hist, edaUni$scores$qq, ncol = 2)
```
`r kfigr::figr(label = "scores_dist", prefix = TRUE, link = TRUE, type="Figure")`: Scores histogram and QQ Plot

```{r scores_box, fig.height=4}
edaUni$scores$box
```
`r kfigr::figr(label = "scores_box", prefix = TRUE, link = TRUE, type="Figure")`: Scores boxplot

**Central Tendency**: The summary statistics (`r kfigr::figr(label = "scores_stats", prefix = TRUE, link = TRUE, type="Table")`) `r edaUni$scores$central`

**Dispersion**: `r edaUni$scores$disp`

**Shape of Distribution**:  `r edaUni$scores$skew` `r edaUni$scores$kurt` The histogram and QQ plot in `r kfigr::figr(label = "scores_dist", prefix = TRUE, link = TRUE, type="Figure")` reveals a left skewed distribution that approximates normality.  

**Outliers**: The boxplot in `r kfigr::figr(label = "scores_box", prefix = TRUE, link = TRUE, type="Figure")`, which graphically depicts the median, the IQR, and maximum and minimum values, suggested that `r ifelse(nrow(edaUni$scores$outliers) == 0, "no", " ")` outliers were extant. `r edaUni$scores$out` 

#### Log Scores
This is a log transformation of scores variable.

`r kfigr::figr(label = "scores_log_stats", prefix = TRUE, link = TRUE, type="Table")`: Log scores summary statistics
```{r scores_log_stats}
knitr::kable(edaUni$scoresLog$stats, digits = 2) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

```{r scores_log_dist}
gridExtra::grid.arrange(edaUni$scoresLog$hist, edaUni$scoresLog$qq, ncol = 2)
```
`r kfigr::figr(label = "scores_log_dist", prefix = TRUE, link = TRUE, type="Figure")`: Log scores histogram and QQ Plot

```{r scores_log_box, fig.height=4}
edaUni$scoresLog$box
```
`r kfigr::figr(label = "scores_log_box", prefix = TRUE, link = TRUE, type="Figure")`: Log scores boxplot

**Central Tendency**: The summary statistics (`r kfigr::figr(label = "scores_log_stats", prefix = TRUE, link = TRUE, type="Table")`) `r edaUni$scoresLog$central`

**Dispersion**: `r edaUni$scoresLog$disp`

**Shape of Distribution**:  `r edaUni$scoresLog$skew` `r edaUni$scoresLog$kurt` The histogram and QQ plot in `r kfigr::figr(label = "scores_log_dist", prefix = TRUE, link = TRUE, type="Figure")` reveals a left skewed distribution that departs rather significantly from normality.

**Outliers**: The boxplot in `r kfigr::figr(label = "scores_log_box", prefix = TRUE, link = TRUE, type="Figure")`, which graphically depicts the median, the IQR, and maximum and minimum values, suggested that `r ifelse(nrow(edaUni$scoresLog$outliers) == 0, "no", " ")` outliers were extant. `r edaUni$scoresLog$out` 

#### Runtime
Total lifetime was obtained for a subset of 100 randomly selected films from the movie data set. This is an analysis of runtime for this random sampling.

`r kfigr::figr(label = "runtime_stats", prefix = TRUE, link = TRUE, type="Table")`: Runtime summary statistics
```{r runtime_stats}
knitr::kable(edaUni$runtime$stats, digits = 2) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

```{r runtime_dist}
gridExtra::grid.arrange(edaUni$runtime$hist, edaUni$runtime$qq, ncol = 2)
```
`r kfigr::figr(label = "runtime_dist", prefix = TRUE, link = TRUE, type="Figure")`: Runtime histogram and QQ Plot

```{r runtime_box, fig.height=4}
edaUni$runtime$box
```
`r kfigr::figr(label = "runtime_box", prefix = TRUE, link = TRUE, type="Figure")`: Runtime boxplot

**Central Tendency**: The summary statistics (`r kfigr::figr(label = "runtime_stats", prefix = TRUE, link = TRUE, type="Table")`) `r edaUni$runtime$central`

**Dispersion**: `r edaUni$runtime$disp`

**Shape of Distribution**:  `r edaUni$runtime$skew` `r edaUni$runtime$kurt` The histogram and QQ plot in `r kfigr::figr(label = "runtime_dist", prefix = TRUE, link = TRUE, type="Figure")` reveals a left skewed distribution that departs significantly from normality.

**Outliers**: The boxplot in `r kfigr::figr(label = "runtime_box", prefix = TRUE, link = TRUE, type="Figure")`, which graphically depicts the median, the IQR, and maximum and minimum values, suggested that `r ifelse(nrow(edaUni$runtime$outliers) == 0, "no", " ")` outliers were extant. `r edaUni$runtime$out` 

#### Theatre Days
This variable captured the number of days between theatrical and dvd release

`r kfigr::figr(label = "thtr_days_stats", prefix = TRUE, link = TRUE, type="Table")`: Theatre says summary statistics
```{r thtr_days_stats}
knitr::kable(edaUni$thtr_days$stats, digits = 2) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

```{r thtr_days_dist}
gridExtra::grid.arrange(edaUni$thtrDays$hist, edaUni$thtrDays$qq, ncol = 2)
```
`r kfigr::figr(label = "thtr_days_dist", prefix = TRUE, link = TRUE, type="Figure")`: Theatre days histogram and QQ Plot

```{r thtr_days_box, fig.height=4}
edaUni$thtr_days$box
```
`r kfigr::figr(label = "thtr_days_box", prefix = TRUE, link = TRUE, type="Figure")`: Theatre days boxplot

**Central Tendency**: The summary statistics (`r kfigr::figr(label = "thtr_days_stats", prefix = TRUE, link = TRUE, type="Table")`) `r edaUni$thtr_days$central`

**Dispersion**: `r edaUni$thtr_days$disp`

**Shape of Distribution**:  `r edaUni$thtr_days$skew` `r edaUni$thtr_days$kurt` The histogram and QQ plot in `r kfigr::figr(label = "thtr_days_dist", prefix = TRUE, link = TRUE, type="Figure")` reveals a left skewed distribution that departs significantly from normality.

**Outliers**: The boxplot in `r kfigr::figr(label = "thtr_days_box", prefix = TRUE, link = TRUE, type="Figure")`, which graphically depicts the median, the IQR, and maximum and minimum values, suggested that `r ifelse(nrow(edaUni$thtr_days$outliers) == 0, "no", " ")` outliers were extant. `r edaUni$thtr_days$out` 

#### Box Office
Total lifetime box office revenue was obtained for a subset of 100 randomly selected films from the movie data set. This is an analysis of box office revenue for this random sampling.

`r kfigr::figr(label = "box_office_stats", prefix = TRUE, link = TRUE, type="Table")`: Box office revenue summary statistics
```{r box_office_stats}
knitr::kable(edaUni$boxOffice$stats, digits = 2) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

```{r box_office_dist}
gridExtra::grid.arrange(edaUni$boxOffice$hist, edaUni$boxOffice$qq, ncol = 2)
```
`r kfigr::figr(label = "box_office_dist", prefix = TRUE, link = TRUE, type="Figure")`: Box office revenue histogram and QQ Plot

```{r box_office_box, fig.height=4}
edaUni$boxOffice$box
```
`r kfigr::figr(label = "box_office_box", prefix = TRUE, link = TRUE, type="Figure")`: Box office revenue boxplot

**Central Tendency**: The summary statistics (`r kfigr::figr(label = "box_office_stats", prefix = TRUE, link = TRUE, type="Table")`) `r edaUni$boxOffice$central`

**Dispersion**: `r edaUni$boxOffice$disp`

**Shape of Distribution**:  `r edaUni$boxOffice$skew` `r edaUni$boxOffice$kurt` The histogram and QQ plot in `r kfigr::figr(label = "box_office_dist", prefix = TRUE, link = TRUE, type="Figure")` reveals a left skewed distribution that departs significantly from normality.

**Outliers**: The boxplot in `r kfigr::figr(label = "box_office_box", prefix = TRUE, link = TRUE, type="Figure")`, which graphically depicts the median, the IQR, and maximum and minimum values, suggested that `r ifelse(nrow(edaUni$boxOffice$outliers) == 0, "no", " ")` outliers were extant. `r edaUni$boxOffice$out` 

#### Log Box Office
This is a log transformation of the box office variable.

`r kfigr::figr(label = "box_office_log_stats", prefix = TRUE, link = TRUE, type="Table")`: Log box office revenue summary statistics
```{r box_office_log_stats}
knitr::kable(edaUni$boxOfficeLog$stats, digits = 2) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

```{r box_office_log_dist}
gridExtra::grid.arrange(edaUni$boxOfficeLog$hist, edaUni$boxOfficeLog$qq, ncol = 2)
```
`r kfigr::figr(label = "box_office_log_dist", prefix = TRUE, link = TRUE, type="Figure")`: Log box office revenue histogram and QQ Plot

```{r box_office_log_box, fig.height=4}
edaUni$boxOfficeLog$box
```
`r kfigr::figr(label = "box_office_log_box", prefix = TRUE, link = TRUE, type="Figure")`: Log box office revenue boxplot

**Central Tendency**: The summary statistics (`r kfigr::figr(label = "box_office_log_stats", prefix = TRUE, link = TRUE, type="Table")`) `r edaUni$boxOfficeLog$central`

**Dispersion**: `r edaUni$boxOfficeLog$disp`

**Shape of Distribution**:  `r edaUni$boxOfficeLog$skew` `r edaUni$boxOfficeLog$kurt` The histogram and QQ plot in `r kfigr::figr(label = "box_office_log_dist", prefix = TRUE, link = TRUE, type="Figure")` reveals a left skewed distribution that approximates normality.  

**Outliers**: The boxplot in `r kfigr::figr(label = "box_office_log_box", prefix = TRUE, link = TRUE, type="Figure")`, which graphically depicts the median, the IQR, and maximum and minimum values, suggested that `r ifelse(nrow(edaUni$boxOfficeLog$outliers) == 0, "no", " ")` outliers were extant. `r edaUni$boxOfficeLog$out` 


## Bivariate Analysis
### Dependent Variable
As mentioned above, the first objective was to identify an available variable that would proxy for box office success. Correlation tests were conducted between the quantitative variables and the log of box office revenue. The top 5 variables most highly correlated with log of box office revenue are summarized in 
`r kfigr::figr(label = "correlation1", prefix = TRUE, link = TRUE, type="Table")`.

`r kfigr::figr(label = "correlation1", prefix = TRUE, link = TRUE, type="Table")` Top 5 variables most highly correlated with box office revenue
```{r correlation1}
mData <- process(mdb2, y = "box_office_log")
cData <- correlate(x = mData$numeric, y = mData$dependent, yLab = "Log Box Office", plot = FALSE)
knitr::kable(head(cData$tests, 10), digits = 2) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
``` 

```{r correlationPlots1, fig.height=10}
gridExtra::grid.arrange(grobs = cData$sPlots, ncol = 2)
```
`r kfigr::figr(label = "correlationPlots1", prefix = TRUE, link = TRUE, type="Figure")`: Scatterplots of variables most highly correlated with log of box office revenue

The scatter plots  in `r kfigr::figr(label = "correlationPlots1", prefix = TRUE, link = TRUE, type="Figure")`, confirmed it.  The log of the number of IMDB votes would proxy for box office revenue and correlation with this dependent variable was the focus of the bivariate analysis that follows.

### Categorical Variable Analysis
Association tests were conducted between the categorical variables and the log number of IMDB votes and `r kfigr::figr(label = "association", prefix = TRUE, link = TRUE, type="Table")` summarizes the most highly associated variables.

`r kfigr::figr(label = "association", prefix = TRUE, link = TRUE, type="Table")` Categorical variables most highly associated with the log number of IMDB votes.
```{r association}
mData <- process(mdb, y = "imdb_num_votes_log")
aData <- associate(x = mData$categorical, y = mData$dependent, yLab = "Log IMDB Votes")
aDataOneWay <- aData %>% filter()
knitr::kable(head(aData$tests, 10), digits = 2) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```
 

As expected, director and studio were highly associated with film popularity.

### Quantitative Variable Analysis 
The correlations between the quantitative variables and the log number of IMDB votes are listed in `r kfigr::figr(label = "correlation2", prefix = TRUE, link = TRUE, type="Table")` in order of highest to lowest correlation.

`r kfigr::figr(label = "correlation2", prefix = TRUE, link = TRUE, type="Table")` Top quantitative variables most highly correlated  with the log number of IMDB votes.
```{r correlation2}
mData <- process(mdb, "imdb_num_votes_log")
cData <- correlate(x = mData$numeric, y = mData$dependent, yLab = "Log IMDB Votes", plot = FALSE)
knitr::kable(head(cData$tests, 10), digits = 2) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

The log of cast votes was highly correlated with the log number of IMDB votes; whereas cast experience was significantly less correlated. Surprisingly, the number of days between the dvd release and the theatrical release was negatively correlated with IMDB votes, causing one to consider the proportion of IMDB votes cast by DVD viewers. 

* * *

# Part 4: Modeling
Developing a linear model that can be used to effectively predict box office performance is the focus of this section. As such, full model feature selection, model selection, model diagnostics, and model interpretation are covered here in detail.

## Full Model Feature Selection.
In the prior section, association and correlation tests were conducted with a 95% confidence level. All categorical variables would remain in the model. The following quantitative variables were removed because they were redundant with other variables with higher correlation with dependent variable:  
* imdb_num_votes - redundant with the dependent variable, its log transformation
* cast_votes - redundant with cast_votes_log, which has a higher correlation


`r kfigr::figr(label = "fullModel", prefix = TRUE, link = TRUE, type="Table")`: Full Model
```{r fullModel}
fm <- fullModel(aData$tests, cData$tests)
knitr::kable(fm, digits = 2) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

The correlations between the quantitative variables are rendered to support the model selection process.

```{r cplot}
mData <- process(mdb, "imdb_num_votes_log")
cData <- correlate(x = mData$numeric, y = mData$dependent, yLab = "Log IMDB Votes", plot = TRUE)
```
`r kfigr::figr(label = "cplot", prefix = TRUE, link = TRUE, type="Figure")` The correlations between the quantitative independent variables

**Rationale**: For the purposes of model selection, all variables with an association or correlation p.value > 0.5 were included in the model. There was no effort made to eliminate variables with minor associations/correlations at this stage.  Including a variable, regardless of its degree of association/correlation allowed the model selection process to consider interactions between two or more variables that may not have been uncovered heretofore. 

## Model Selection
Starting with the full model described above, both forward selection and backward elimination methods to determine if two different models emerged from the process, then to evaluate the performance of those models. 
The correlation plot 

`r kfigr::figr(label = "corrPlot", prefix = TRUE, link = TRUE, type="Table")` Top quantitative variables most highly correlated  with the log number of IMDB votes.
```{r corrPlot}
mData <- process(mdb, "imdb_num_votes_log")
cData <- correlate(x = mData$numeric, y = mData$dependent, yLab = "Log IMDB Votes", plot = FALSE)
knitr::kable(head(cData$tests, 10), digits = 2) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

`r kfigr::figr(label = "forward", prefix = TRUE, link = TRUE, type="Table")`: Forward Selection Prediction Model
```{r forward, results = "html"}
#forwardSelection <- movies::forward(movies)
#summary(forwardSelection)
```

`r kfigr::figr(label = "back", prefix = TRUE, link = TRUE, type="Table")`: Backward Elimination Prediction Model
```{r back, results = "html"}
#backStep <- movies::back(movies)
#summary(backStep)
```
* * *

# Part 5: Prediction

NOTE: Insert code chunks as needed by clicking on the "Insert a new code chunk" 
button above. Make sure that your code is visible in the project you submit. 
Delete this note when before you submit your work.

* * *

# Part 6: Conclusion

# Appendix
## Appendix A: Codebook
`r kfigr::figr(label = "codebook", prefix = TRUE, link = TRUE, type="Table")`: Movie data set codebook
```{r codebook}
codebook <- openxlsx::read.xlsx("../data/features.xlsx", sheet = 1)
codebook <- codebook %>% select(Source, Type, Variable, Description)
knitr::kable(codebook, align = 'l') %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center") %>%
  kableExtra::group_rows("General", 1,7) %>%
  kableExtra::group_rows("Organization", 8,14) %>%
  kableExtra::group_rows("Dates", 15,21) %>%
  kableExtra::group_rows("Experience", 22,23) %>%
  kableExtra::group_rows("Performance", 24,38) %>%
  kableExtra::group_rows("Interaction", 39,40) %>%
  kableExtra::group_rows("Box Office", 41,42) 
```

## Appendix B: Univariate Analysis
### Best Director / Actor / Actress 
As indicated in `r kfigr::figr(label = "a_best_actor", prefix = TRUE, link = TRUE, type="Figure")`, the percentages of films with best director, actor and actress oscars were `r edaUni$bestDirWin$stats$Proportion[2] * 100`%, `r edaUni$bestActorWin$stats$Proportion[2] * 100`%,  and `r edaUni$bestActressWin$stats$Proportion[2] * 100`%, respectively.  Again, these proportions indicate that oscar awards would not be a good predictor of movie popularity. The bivariate analysis will explore this further.


```{r a_best_actor}
gridExtra::grid.arrange(edaUni$bestDirWin$plot, edaUni$bestActorWin$plot, edaUni$bestActressWin$plot, ncol = 3)
```
`r kfigr::figr(label = "a_best_actor", prefix = TRUE, link = TRUE, type="Figure")`: Best director/actor/actress 

### Best Picture 
Since the proportion of films nominated for and winning best picture were so small, this variable was not likely to be a good predictor of movie popularity. The bivariate analysis below will illuminate this further.

```{r a_best_picture}
gridExtra::grid.arrange(edaUni$bestPicNom$plot, edaUni$bestPicWin$plot, ncol = 2)
```
`r kfigr::figr(label = "a_best_picture", prefix = TRUE, link = TRUE, type="Figure")`: Best picture nominations and wins

### Genre
The drama genre represented a plurality of the releases in the sample, followed by comedy action & adventure then mystery & suspense. The top four genres account for nearly `r round(sum(head(edaUni$genre$stats %>% arrange(desc(Proportion)) %>% select(Proportion), 4)) * 100, -1)`% of the films in the sample. 
```{r a_genre}
edaUni$genre$plot
```
`r kfigr::figr(label = "a_genre", prefix = TRUE, link = TRUE, type="Figure")`: Films by genre

### MPAA Rating
Rated R films accounted for over `r round(edaUni$mpaa$stats$Proportion[5] * 100, -1)`% of the releases, followed by PG and PG-13. Collectively, R, PG, and PG-13 rated films represent `r round(sum(head(edaUni$mpaa$stats %>% arrange(desc(Proportion)) %>% select(Proportion), 3)) * 100, -1)`% of the films in the sample. NC-17 films were excluded from this analysis.
```{r a_mpaa}
edaUni$mpaa$plot
```
`r kfigr::figr(label = "a_mpaa", prefix = TRUE, link = TRUE, type="Figure")`: Films by MPAA Rating

### Month of Theatrical Release
The plurality of features in the sample (`r sum(edaUni$month$stats$Proportion[c(1,6,10,12)])*100`%) were released during the months of January, June, October and December.  
```{r a_month}
edaUni$month$plot
```
`r kfigr::figr(label = "a_month", prefix = TRUE, link = TRUE, type="Figure")`: Theatrical releases by month

### Season of Theatrical Release
The plurality of features in the sample were released during the fall and summer months with over `r round(edaUni$season$stats$Proportion[3] *100, -1)`% opening in the month of December alone. 
```{r a_season}
edaUni$season$plot
```
`r kfigr::figr(label = "a_season", prefix = TRUE, link = TRUE, type="Figure")`: Theatrical releases by season

### Audience Scores
This variable captured the audience scores from Rotten Tomatoes for each film

`r kfigr::figr(label = "a_audience_scores_stats", prefix = TRUE, link = TRUE, type="Table")`: Audience score summary statistics
```{r a_audience_scores_stats}
knitr::kable(edaUni$audienceScores$stats, digits = 2) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

```{r a_audience_scores_dist}
gridExtra::grid.arrange(edaUni$audienceScores$hist, edaUni$audienceScores$qq, ncol = 2)
```
`r kfigr::figr(label = "a_audience_scores_dist", prefix = TRUE, link = TRUE, type="Figure")`: Audience score histogram and QQ Plot

```{r a_audience_scores_box, fig.height=4}
edaUni$audienceScores$box
```
`r kfigr::figr(label = "a_audience_scores_box", prefix = TRUE, link = TRUE, type="Figure")`: Audience score boxplot

**Central Tendency**: The summary statistics (`r kfigr::figr(label = "a_audience_scores_stats", prefix = TRUE, link = TRUE, type="Table")`) `r edaUni$audienceScores$central`

**Dispersion**: `r edaUni$audienceScores$disp`

**Shape of Distribution**:  `r edaUni$audienceScores$skew` `r edaUni$audienceScores$kurt` The histogram and QQ plot in `r kfigr::figr(label = "a_audience_scores_dist", prefix = TRUE, link = TRUE, type="Figure")` reveals a left skewed distribution that departs from normality.  

**Outliers**: The boxplot in `r kfigr::figr(label = "a_audience_scores_box", prefix = TRUE, link = TRUE, type="Figure")`, which graphically depicts the median, the IQR, and maximum and minimum values, suggested that `r ifelse(nrow(edaUni$audienceScores$outliers) == 0, "no", " ")` outliers were extant. `r edaUni$audienceScores$out` 

### Box Office
Total lifetime box office revenue was obtained for a subset of 100 randomly selected films from the movie data set. This is an analysis of box office revenue for this random sampling.

`r kfigr::figr(label = "a_box_office_stats", prefix = TRUE, link = TRUE, type="Table")`: Box office revenue summary statistics
```{r a_box_office_stats}
knitr::kable(edaUni$boxOffice$stats, digits = 2) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

```{r a_box_office_dist}
gridExtra::grid.arrange(edaUni$boxOffice$hist, edaUni$boxOffice$qq, ncol = 2)
```
`r kfigr::figr(label = "a_box_office_dist", prefix = TRUE, link = TRUE, type="Figure")`: Box office revenue histogram and QQ Plot

```{r a_box_office_box, fig.height=4}
edaUni$boxOffice$box
```
`r kfigr::figr(label = "a_box_office_box", prefix = TRUE, link = TRUE, type="Figure")`: Box office revenue boxplot

**Central Tendency**: The summary statistics (`r kfigr::figr(label = "a_box_office_stats", prefix = TRUE, link = TRUE, type="Table")`) `r edaUni$boxOffice$central`

**Dispersion**: `r edaUni$boxOffice$disp`

**Shape of Distribution**:  `r edaUni$boxOffice$skew` `r edaUni$boxOffice$kurt` The histogram and QQ plot in `r kfigr::figr(label = "a_box_office_dist", prefix = TRUE, link = TRUE, type="Figure")` reveals a left skewed distribution that departs significantly from normality.

**Outliers**: The boxplot in `r kfigr::figr(label = "a_box_office_box", prefix = TRUE, link = TRUE, type="Figure")`, which graphically depicts the median, the IQR, and maximum and minimum values, suggested that `r ifelse(nrow(edaUni$boxOffice$outliers) == 0, "no", " ")` outliers were extant. `r edaUni$boxOffice$out` 

### Log Box Office
This is a log transformation of the box office variable.

`r kfigr::figr(label = "a_box_office_log_stats", prefix = TRUE, link = TRUE, type="Table")`: Log box office revenue summary statistics
```{r a_box_office_log_stats}
knitr::kable(edaUni$boxOfficeLog$stats, digits = 2) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

```{r a_box_office_log_dist}
gridExtra::grid.arrange(edaUni$boxOfficeLog$hist, edaUni$boxOfficeLog$qq, ncol = 2)
```
`r kfigr::figr(label = "a_box_office_log_dist", prefix = TRUE, link = TRUE, type="Figure")`: Log box office revenue histogram and QQ Plot

```{r a_box_office_log_box, fig.height=4}
edaUni$boxOfficeLog$box
```
`r kfigr::figr(label = "a_box_office_log_box", prefix = TRUE, link = TRUE, type="Figure")`: Log box office revenue boxplot

**Central Tendency**: The summary statistics (`r kfigr::figr(label = "a_box_office_log_stats", prefix = TRUE, link = TRUE, type="Table")`) `r edaUni$boxOfficeLog$central`

**Dispersion**: `r edaUni$boxOfficeLog$disp`

**Shape of Distribution**:  `r edaUni$boxOfficeLog$skew` `r edaUni$boxOfficeLog$kurt` The histogram and QQ plot in `r kfigr::figr(label = "a_box_office_log_dist", prefix = TRUE, link = TRUE, type="Figure")` reveals a left skewed distribution that approximates normality.  

**Outliers**: The boxplot in `r kfigr::figr(label = "a_box_office_log_box", prefix = TRUE, link = TRUE, type="Figure")`, which graphically depicts the median, the IQR, and maximum and minimum values, suggested that `r ifelse(nrow(edaUni$boxOfficeLog$outliers) == 0, "no", " ")` outliers were extant. `r edaUni$boxOfficeLog$out` 

### Cast Experience
This derived variable measured the relative experience of a given cast and was defined as the sum of the observations for the cast associated with each film.  

`r kfigr::figr(label = "a_cast_experience_stats", prefix = TRUE, link = TRUE, type="Table")`: Cast experience summary statistics
```{r a_cast_experience_stats}
knitr::kable(edaUni$castExperience$stats, digits = 2) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

```{r a_cast_experience_dist}
gridExtra::grid.arrange(edaUni$castExperience$hist, edaUni$castExperience$qq, ncol = 2)
```
`r kfigr::figr(label = "a_cast_experience_dist", prefix = TRUE, link = TRUE, type="Figure")`: Cast experience histogram and QQ Plot

```{r a_cast_experience_box, fig.height=4}
edaUni$castExperience$box
```
`r kfigr::figr(label = "a_cast_experience_box", prefix = TRUE, link = TRUE, type="Figure")`: Cast experience boxplot

**Central Tendency**: The summary statistics (`r kfigr::figr(label = "a_cast_experience_stats", prefix = TRUE, link = TRUE, type="Table")`) `r edaUni$castExperience$central`

**Dispersion**: `r edaUni$castExperience$disp`

**Shape of Distribution**:  `r edaUni$castExperience$skew` `r edaUni$castExperience$kurt` The histogram and QQ plot in `r kfigr::figr(label = "a_cast_experience_dist", prefix = TRUE, link = TRUE, type="Figure")` reveal a distribution which departs significantly from normality.

**Outliers**: The boxplot in `r kfigr::figr(label = "a_cast_experience_box", prefix = TRUE, link = TRUE, type="Figure")`, which graphically depicts the median, the IQR, and maximum and minimum values, suggested that `r ifelse(nrow(edaUni$castExperience$outliers) == 0, "no", " ")` outliers were extant. `r edaUni$castExperience$out` Given the proximity of the outliers to the 1.5xIQR, no effort was made to remove them.

### Log Cast Experience
This variable is a log transformation of the cast experience variable

`r kfigr::figr(label = "a_cast_experience_log_stats", prefix = TRUE, link = TRUE, type="Table")`: Cast experience summary statistics
```{r a_cast_experience_log_stats}
knitr::kable(edaUni$castExperienceLog$stats, digits = 2) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

```{r a_cast_experience_log_dist}
gridExtra::grid.arrange(edaUni$castExperienceLog$hist, edaUni$castExperienceLog$qq, ncol = 2)
```
`r kfigr::figr(label = "a_cast_experience_log_dist", prefix = TRUE, link = TRUE, type="Figure")`: Cast experience histogram and QQ Plot

```{r a_cast_experience_log_box, fig.height=4}
edaUni$castExperienceLog$box
```
`r kfigr::figr(label = "a_cast_experience_log_box", prefix = TRUE, link = TRUE, type="Figure")`: Cast experience boxplot

**Central Tendency**: The summary statistics (`r kfigr::figr(label = "a_cast_experience_log_stats", prefix = TRUE, link = TRUE, type="Table")`) `r edaUni$castExperienceLog$central`

**Dispersion**: `r edaUni$castExperienceLog$disp`

**Shape of Distribution**:  `r edaUni$castExperienceLog$skew` `r edaUni$castExperienceLog$kurt` The histogram and QQ plot in `r kfigr::figr(label = "a_cast_experience_log_dist", prefix = TRUE, link = TRUE, type="Figure")` reveal a distribution which departs significantly from normality.

**Outliers**: The boxplot in `r kfigr::figr(label = "a_cast_experience_log_box", prefix = TRUE, link = TRUE, type="Figure")`, which graphically depicts the median, the IQR, and maximum and minimum values, suggested that `r ifelse(nrow(edaUni$castExperienceLog$outliers) == 0, "no", " ")` outliers were extant. `r edaUni$castExperienceLog$out` Given the proximity of the outliers to the 1.5xIQR, no effort was made to remove them.

### Cast Votes
This variable captured the total number of votes allocated to each cast member for a film. 

`r kfigr::figr(label = "a_cast_votes_stats", prefix = TRUE, link = TRUE, type="Table")`: Cast votes summary statistics
```{r a_cast_votes_stats}
knitr::kable(edaUni$castVotes$stats, digits = 2) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

```{r a_cast_votes_dist}
gridExtra::grid.arrange(edaUni$castVotes$hist, edaUni$castVotes$qq, ncol = 2)
```
`r kfigr::figr(label = "a_cast_votes_dist", prefix = TRUE, link = TRUE, type="Figure")`: Cast votes histogram and QQ Plot

```{r a_cast_votes_box, fig.height=4}
edaUni$castVotes$box
```
`r kfigr::figr(label = "a_cast_votes_box", prefix = TRUE, link = TRUE, type="Figure")`: Cast votes boxplot

**Central Tendency**: The summary statistics (`r kfigr::figr(label = "a_cast_votes_stats", prefix = TRUE, link = TRUE, type="Table")`) `r edaUni$castVotes$central`

**Dispersion**: `r edaUni$castVotes$disp`

**Shape of Distribution**:  `r edaUni$castVotes$skew` `r edaUni$castVotes$kurt` The histogram and QQ plot in `r kfigr::figr(label = "a_cast_votes_dist", prefix = TRUE, link = TRUE, type="Figure")` reveals a left skewed distribution that departs significantly from normality.  

**Outliers**: The boxplot in `r kfigr::figr(label = "a_cast_votes_box", prefix = TRUE, link = TRUE, type="Figure")`, which graphically depicts the median, the IQR, and maximum and minimum values, suggested that `r ifelse(nrow(edaUni$castVotes$outliers) == 0, "no", " ")` outliers were extant. `r edaUni$castVotes$out` 

### Log Cast Votes
This is a log transformation of the cast votes variable.

`r kfigr::figr(label = "a_cast_votes_log_stats", prefix = TRUE, link = TRUE, type="Table")`: Log cast votes summary statistics
```{r a_cast_votes_log_stats}
knitr::kable(edaUni$castVotesLog$stats, digits = 2) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

```{r a_cast_votes_log_dist}
gridExtra::grid.arrange(edaUni$castVotesLog$hist, edaUni$castVotesLog$qq, ncol = 2)
```
`r kfigr::figr(label = "a_cast_votes_log_dist", prefix = TRUE, link = TRUE, type="Figure")`: Log cast votes histogram and QQ Plot

```{r a_cast_votes_log_box, fig.height=4}
edaUni$castVotesLog$box
```
`r kfigr::figr(label = "a_cast_votes_log_box", prefix = TRUE, link = TRUE, type="Figure")`: Log cast votes boxplot

**Central Tendency**: The summary statistics (`r kfigr::figr(label = "a_cast_votes_log_stats", prefix = TRUE, link = TRUE, type="Table")`) `r edaUni$castVotesLog$central`

**Dispersion**: `r edaUni$castVotesLog$disp`

**Shape of Distribution**:  `r edaUni$castVotesLog$skew` `r edaUni$castVotesLog$kurt` The histogram and QQ plot in `r kfigr::figr(label = "a_cast_votes_log_dist", prefix = TRUE, link = TRUE, type="Figure")` reveals a left skewed distribution that approximates normality.  

**Outliers**: The boxplot in `r kfigr::figr(label = "a_cast_votes_log_box", prefix = TRUE, link = TRUE, type="Figure")`, which graphically depicts the median, the IQR, and maximum and minimum values, suggested that `r ifelse(nrow(edaUni$castVotesLog$outliers) == 0, "no", " ")` outliers were extant. `r edaUni$castVotesLog$out` 

### Critics Scores
This variable captured the critics scores for each film

`r kfigr::figr(label = "a_critics_scores_stats", prefix = TRUE, link = TRUE, type="Table")`: Critics score summary statistics
```{r a_critics_scores_stats}
knitr::kable(edaUni$criticsScores$stats, digits = 2) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

```{r a_critics_scores_dist}
gridExtra::grid.arrange(edaUni$criticsScores$hist, edaUni$criticsScores$qq, ncol = 2)
```
`r kfigr::figr(label = "a_critics_scores_dist", prefix = TRUE, link = TRUE, type="Figure")`: Critics score histogram and QQ Plot

```{r a_critics_scores_box, fig.height=4}
edaUni$criticsScores$box
```
`r kfigr::figr(label = "a_critics_scores_box", prefix = TRUE, link = TRUE, type="Figure")`: Critics score boxplot

**Central Tendency**: The summary statistics (`r kfigr::figr(label = "a_critics_scores_stats", prefix = TRUE, link = TRUE, type="Table")`) `r edaUni$criticsScores$central`

**Dispersion**: `r edaUni$criticsScores$disp`

**Shape of Distribution**:  `r edaUni$criticsScores$skew` `r edaUni$criticsScores$kurt` The histogram and QQ plot in `r kfigr::figr(label = "a_critics_scores_dist", prefix = TRUE, link = TRUE, type="Figure")` reveals a left skewed distribution that departs from normality.  

**Outliers**: The boxplot in `r kfigr::figr(label = "a_critics_scores_box", prefix = TRUE, link = TRUE, type="Figure")`, which graphically depicts the median, the IQR, and maximum and minimum values, suggested that `r ifelse(nrow(edaUni$criticsScores$outliers) == 0, "no", " ")` outliers were extant. `r edaUni$criticsScores$out` 

#### Director Experience
This derived variable measured the relative experience of a given director and was defined as the sum of the observations for the director associated with each film.  

`r kfigr::figr(label = "a_director_experience_stats", prefix = TRUE, link = TRUE, type="Table")`: Director experience summary statistics
```{r a_director_experience_stats}
knitr::kable(edaUni$directorExperience$stats, digits = 2) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

```{r a_director_experience_dist}
gridExtra::grid.arrange(edaUni$directorExperience$hist, edaUni$directorExperience$qq, ncol = 2)
```
`r kfigr::figr(label = "a_director_experience_dist", prefix = TRUE, link = TRUE, type="Figure")`: Director experience histogram and QQ Plot

```{r a_director_experience_box, fig.height=4}
edaUni$directorExperience$box
```
`r kfigr::figr(label = "a_director_experience_box", prefix = TRUE, link = TRUE, type="Figure")`: Director experience boxplot

**Central Tendency**: The summary statistics (`r kfigr::figr(label = "a_director_experience_stats", prefix = TRUE, link = TRUE, type="Table")`) `r edaUni$directorExperience$central`

**Dispersion**: `r edaUni$directorExperience$disp`

**Shape of Distribution**:  `r edaUni$directorExperience$skew` `r edaUni$directorExperience$kurt` The histogram and QQ plot in `r kfigr::figr(label = "a_director_experience_dist", prefix = TRUE, link = TRUE, type="Figure")` reveal a distribution which departs significantly from normality.

**Outliers**: The boxplot in `r kfigr::figr(label = "a_director_experience_box", prefix = TRUE, link = TRUE, type="Figure")`, which graphically depicts the median, the IQR, and maximum and minimum values, suggested that `r ifelse(nrow(edaUni$directorExperience$outliers) == 0, "no", " ")` outliers were extant. `r edaUni$directorExperience$out` Given the proximity of the outliers to the 1.5xIQR, no effort was made to remove them.

### Log Director Experience
This variable was a log transformation of the director experience variable.

`r kfigr::figr(label = "a_director_experience_log_stats", prefix = TRUE, link = TRUE, type="Table")`: Log director experience summary statistics
```{r a_director_experience_log_stats}
knitr::kable(edaUni$directorExperienceLog$stats, digits = 2) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

```{r a_director_experience_log_dist}
gridExtra::grid.arrange(edaUni$directorExperienceLog$hist, edaUni$directorExperienceLog$qq, ncol = 2)
```
`r kfigr::figr(label = "a_director_experience_log_dist", prefix = TRUE, link = TRUE, type="Figure")`: Log director experience histogram and QQ Plot

```{r a_director_experience_log_box, fig.height=4}
edaUni$directorExperienceLog$box
```
`r kfigr::figr(label = "a_director_experience_log_box", prefix = TRUE, link = TRUE, type="Figure")`: Log director experience boxplot

**Central Tendency**: The summary statistics (`r kfigr::figr(label = "a_director_experience_log_stats", prefix = TRUE, link = TRUE, type="Table")`) `r edaUni$directorExperienceLog$central`

**Dispersion**: `r edaUni$directorExperienceLog$disp`

**Shape of Distribution**:  `r edaUni$directorExperienceLog$skew` `r edaUni$directorExperienceLog$kurt` The histogram and QQ plot in `r kfigr::figr(label = "a_director_experience_log_dist", prefix = TRUE, link = TRUE, type="Figure")` reveal a distribution which departs significantly from normality.

**Outliers**: The boxplot in `r kfigr::figr(label = "a_director_experience_log_box", prefix = TRUE, link = TRUE, type="Figure")`, which graphically depicts the median, the IQR, and maximum and minimum values, suggested that `r ifelse(nrow(edaUni$directorExperienceLog$outliers) == 0, "no", " ")` outliers were extant. `r edaUni$directorExperienceLog$out` Given the proximity of the outliers to the 1.5xIQR, no effort was made to remove them.

### Number of IMDB Votes 
This variable captured the number of IMDB votes cast for each film.

`r kfigr::figr(label = "a_imdb_votes_stats", prefix = TRUE, link = TRUE, type="Table")`: IMDB votes summary statistics
```{r a_imdb_votes_stats}
knitr::kable(edaUni$imdbVotes$stats, digits = 2) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

```{r a_imdb_votes_dist}
gridExtra::grid.arrange(edaUni$imdbVotes$hist, edaUni$imdbVotes$qq, ncol = 2)
```
`r kfigr::figr(label = "a_imdb_votes_dist", prefix = TRUE, link = TRUE, type="Figure")`: IMDB votes histogram and QQ Plot

```{r a_imdb_votes_box, fig.height=4}
edaUni$imdbVotes$box
```
`r kfigr::figr(label = "a_imdb_votes_box", prefix = TRUE, link = TRUE, type="Figure")`: IMDB votes boxplot

**Central Tendency**: The summary statistics (`r kfigr::figr(label = "a_imdb_votes_stats", prefix = TRUE, link = TRUE, type="Table")`) `r edaUni$imdbVotes$central`

**Dispersion**: `r edaUni$imdbVotes$disp`

**Shape of Distribution**:  `r edaUni$imdbVotes$skew` `r edaUni$imdbVotes$kurt` The histogram and QQ plot in `r kfigr::figr(label = "a_imdb_votes_dist", prefix = TRUE, link = TRUE, type="Figure")` reveal a distribution which departs significantly from normality.

**Outliers**: The boxplot in `r kfigr::figr(label = "a_imdb_votes_box", prefix = TRUE, link = TRUE, type="Figure")`, which graphically depicts the median, the IQR, and maximum and minimum values, suggested that `r ifelse(nrow(edaUni$imdbVotes$outliers) == 0, "no", " ")` outliers were extant. `r edaUni$imdbVotes$out` 

### Log Number of IMDB Votes 
This was a log transformation of the IMDB votes variable.

`r kfigr::figr(label = "a_imdb_votes_log_stats", prefix = TRUE, link = TRUE, type="Table")`: Log IMDB votes summary statistics
```{r a_imdb_votes_log_stats}
knitr::kable(edaUni$imdbVotesLog$stats, digits = 2) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

```{r a_imdb_votes_log_dist}
gridExtra::grid.arrange(edaUni$imdbVotesLog$hist, edaUni$imdbVotesLog$qq, ncol = 2)
```
`r kfigr::figr(label = "a_imdb_votes_log_dist", prefix = TRUE, link = TRUE, type="Figure")`: Log IMDB votes histogram and QQ Plot

```{r a_imdb_votes_log_box, fig.height=4}
edaUni$imdbVotesLog$box
```
`r kfigr::figr(label = "a_imdb_votes_log_box", prefix = TRUE, link = TRUE, type="Figure")`: Log IMDB votes boxplot

**Central Tendency**: The summary statistics (`r kfigr::figr(label = "a_imdb_votes_log_stats", prefix = TRUE, link = TRUE, type="Table")`) `r edaUni$imdbVotesLog$central`

**Dispersion**: `r edaUni$imdbVotesLog$disp`

**Shape of Distribution**:  `r edaUni$imdbVotesLog$skew` `r edaUni$imdbVotesLog$kurt` The histogram and QQ plot in `r kfigr::figr(label = "a_imdb_votes_log_dist", prefix = TRUE, link = TRUE, type="Figure")` reveal a nearly normal distribution.

**Outliers**: The boxplot in `r kfigr::figr(label = "a_imdb_votes_log_box", prefix = TRUE, link = TRUE, type="Figure")`, which graphically depicts the median, the IQR, and maximum and minimum values, suggested that `r ifelse(nrow(edaUni$imdbVotesLog$outliers) == 0, "no", " ")` outliers were extant. `r edaUni$imdbVotesLog$out` 

### IMDB Ratings
This variable captured the IMDB rating for each film

`r kfigr::figr(label = "a_imdb_rating_stats", prefix = TRUE, link = TRUE, type="Table")`: IMDB rating summary statistics
```{r a_imdb_rating_stats}
knitr::kable(edaUni$imdbRating$stats, digits = 2) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

```{r a_imdb_rating_dist}
gridExtra::grid.arrange(edaUni$imdbRating$hist, edaUni$imdbRating$qq, ncol = 2)
```
`r kfigr::figr(label = "a_imdb_rating_dist", prefix = TRUE, link = TRUE, type="Figure")`: IMDB rating histogram and QQ Plot

```{r a_imdb_rating_box, fig.height=4}
edaUni$imdbRating$box
```
`r kfigr::figr(label = "a_imdb_rating_box", prefix = TRUE, link = TRUE, type="Figure")`: IMDB rating boxplot

**Central Tendency**: The summary statistics (`r kfigr::figr(label = "a_imdb_rating_stats", prefix = TRUE, link = TRUE, type="Table")`) `r edaUni$imdbRating$central`

**Dispersion**: `r edaUni$imdbRating$disp`

**Shape of Distribution**:  `r edaUni$imdbRating$skew` `r edaUni$imdbRating$kurt` The histogram and QQ plot in `r kfigr::figr(label = "a_imdb_rating_dist", prefix = TRUE, link = TRUE, type="Figure")` reveal a nearly normal distribution.

**Outliers**: The boxplot in `r kfigr::figr(label = "a_imdb_rating_box", prefix = TRUE, link = TRUE, type="Figure")`, which graphically depicts the median, the IQR, and maximum and minimum values, suggested that `r ifelse(nrow(edaUni$imdbRating$outliers) == 0, "no", " ")` outliers were extant. `r edaUni$imdbRating$out` 

### Runtime
This is an analysis of moving runtimes.

`r kfigr::figr(label = "a_runtime_stats", prefix = TRUE, link = TRUE, type="Table")`: Runtime summary statistics
```{r a_runtime_stats}
knitr::kable(edaUni$runtime$stats, digits = 2) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

```{r a_runtime_dist}
gridExtra::grid.arrange(edaUni$runtime$hist, edaUni$runtime$qq, ncol = 2)
```
`r kfigr::figr(label = "a_runtime_dist", prefix = TRUE, link = TRUE, type="Figure")`: Runtime histogram and QQ Plot

```{r a_runtime_box, fig.height=4}
edaUni$runtime$box
```
`r kfigr::figr(label = "a_runtime_box", prefix = TRUE, link = TRUE, type="Figure")`: Runtime boxplot

**Central Tendency**: The summary statistics (`r kfigr::figr(label = "a_runtime_stats", prefix = TRUE, link = TRUE, type="Table")`) `r edaUni$runtime$central`

**Dispersion**: `r edaUni$runtime$disp`

**Shape of Distribution**:  `r edaUni$runtime$skew` `r edaUni$runtime$kurt` The histogram and QQ plot in `r kfigr::figr(label = "a_runtime_dist", prefix = TRUE, link = TRUE, type="Figure")` reveals a left skewed distribution that departs significantly from normality.

**Outliers**: The boxplot in `r kfigr::figr(label = "a_runtime_box", prefix = TRUE, link = TRUE, type="Figure")`, which graphically depicts the median, the IQR, and maximum and minimum values, suggested that `r ifelse(nrow(edaUni$runtime$outliers) == 0, "no", " ")` outliers were extant. `r edaUni$runtime$out` 

### Log Runtime
This is an analysis of the log of moving runtimes.

`r kfigr::figr(label = "a_runtime_log_stats", prefix = TRUE, link = TRUE, type="Table")`: Log runtime summary statistics
```{r a_runtime_log_stats}
knitr::kable(edaUni$runtimeLog$stats, digits = 2) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

```{r a_runtime_log_dist}
gridExtra::grid.arrange(edaUni$runtimeLog$hist, edaUni$runtimeLog$qq, ncol = 2)
```
`r kfigr::figr(label = "a_runtime_log_dist", prefix = TRUE, link = TRUE, type="Figure")`: Log runtime histogram and QQ Plot

```{r a_runtime_log_box, fig.height=4}
edaUni$runtimeLog$box
```
`r kfigr::figr(label = "a_runtime_log_box", prefix = TRUE, link = TRUE, type="Figure")`: Log runtime boxplot

**Central Tendency**: The summary statistics (`r kfigr::figr(label = "a_runtime_log_stats", prefix = TRUE, link = TRUE, type="Table")`) `r edaUni$runtimeLog$central`

**Dispersion**: `r edaUni$runtimeLog$disp`

**Shape of Distribution**:  `r edaUni$runtimeLog$skew` `r edaUni$runtimeLog$kurt` The histogram and QQ plot in `r kfigr::figr(label = "a_runtime_log_dist", prefix = TRUE, link = TRUE, type="Figure")` reveals a left skewed distribution that departs significantly from normality.

**Outliers**: The boxplot in `r kfigr::figr(label = "a_runtime_log_box", prefix = TRUE, link = TRUE, type="Figure")`, which graphically depicts the median, the IQR, and maximum and minimum values, suggested that `r ifelse(nrow(edaUni$runtimeLog$outliers) == 0, "no", " ")` outliers were extant. `r edaUni$runtimeLog$out` 

### Scores
This variable captured the total score for each film defined as 10 * IMDB Rating + critics score + audience_score.

`r kfigr::figr(label = "a_scores_stats", prefix = TRUE, link = TRUE, type="Table")`: Scores summary statistics
```{r a_scores_stats}
knitr::kable(edaUni$scores$stats, digits = 2) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

```{r a_scores_dist}
gridExtra::grid.arrange(edaUni$scores$hist, edaUni$scores$qq, ncol = 2)
```
`r kfigr::figr(label = "a_scores_dist", prefix = TRUE, link = TRUE, type="Figure")`: Scores histogram and QQ Plot

```{r a_scores_box, fig.height=4}
edaUni$scores$box
```
`r kfigr::figr(label = "a_scores_box", prefix = TRUE, link = TRUE, type="Figure")`: Scores boxplot

**Central Tendency**: The summary statistics (`r kfigr::figr(label = "a_scores_stats", prefix = TRUE, link = TRUE, type="Table")`) `r edaUni$scores$central`

**Dispersion**: `r edaUni$scores$disp`

**Shape of Distribution**:  `r edaUni$scores$skew` `r edaUni$scores$kurt` The histogram and QQ plot in `r kfigr::figr(label = "a_scores_dist", prefix = TRUE, link = TRUE, type="Figure")` reveals a left skewed distribution that approximates normality.  

**Outliers**: The boxplot in `r kfigr::figr(label = "a_scores_box", prefix = TRUE, link = TRUE, type="Figure")`, which graphically depicts the median, the IQR, and maximum and minimum values, suggested that `r ifelse(nrow(edaUni$scores$outliers) == 0, "no", " ")` outliers were extant. `r edaUni$scores$out` 

### Log Scores
This is a log transformation of scores variable.

`r kfigr::figr(label = "a_scores_log_stats", prefix = TRUE, link = TRUE, type="Table")`: Log scores summary statistics
```{r a_scores_log_stats}
knitr::kable(edaUni$scoresLog$stats, digits = 2) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

```{r a_scores_log_dist}
gridExtra::grid.arrange(edaUni$scoresLog$hist, edaUni$scoresLog$qq, ncol = 2)
```
`r kfigr::figr(label = "a_scores_log_dist", prefix = TRUE, link = TRUE, type="Figure")`: Log scores histogram and QQ Plot

```{r a_scores_log_box, fig.height=4}
edaUni$scoresLog$box
```
`r kfigr::figr(label = "a_scores_log_box", prefix = TRUE, link = TRUE, type="Figure")`: Log scores boxplot

**Central Tendency**: The summary statistics (`r kfigr::figr(label = "a_scores_log_stats", prefix = TRUE, link = TRUE, type="Table")`) `r edaUni$scoresLog$central`

**Dispersion**: `r edaUni$scoresLog$disp`

**Shape of Distribution**:  `r edaUni$scoresLog$skew` `r edaUni$scoresLog$kurt` The histogram and QQ plot in `r kfigr::figr(label = "a_scores_log_dist", prefix = TRUE, link = TRUE, type="Figure")` reveals a left skewed distribution that departs rather significantly from normality.

**Outliers**: The boxplot in `r kfigr::figr(label = "a_scores_log_box", prefix = TRUE, link = TRUE, type="Figure")`, which graphically depicts the median, the IQR, and maximum and minimum values, suggested that `r ifelse(nrow(edaUni$scoresLog$outliers) == 0, "no", " ")` outliers were extant. `r edaUni$scoresLog$out` 

### Theatre Days
This variable captured the number of days between theatrical and dvd release

`r kfigr::figr(label = "a_thtr_days_stats", prefix = TRUE, link = TRUE, type="Table")`: Theatre says summary statistics
```{r a_thtr_days_stats}
knitr::kable(edaUni$thtrDays$stats, digits = 2) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

```{r a_thtr_days_dist}
gridExtra::grid.arrange(edaUni$thtrDays$hist, edaUni$thtrDays$qq, ncol = 2)
```
`r kfigr::figr(label = "a_thtr_days_dist", prefix = TRUE, link = TRUE, type="Figure")`: Theatre days histogram and QQ Plot

```{r a_thtr_days_box, fig.height=4}
edaUni$thtrDays$box
```
`r kfigr::figr(label = "a_thtr_days_box", prefix = TRUE, link = TRUE, type="Figure")`: Theatre days boxplot

**Central Tendency**: The summary statistics (`r kfigr::figr(label = "a_thtr_days_stats", prefix = TRUE, link = TRUE, type="Table")`) `r edaUni$thtrDays$central`

**Dispersion**: `r edaUni$thtrDays$disp`

**Shape of Distribution**:  `r edaUni$thtrDays$skew` `r edaUni$thtrDays$kurt` The histogram and QQ plot in `r kfigr::figr(label = "a_thtr_days_dist", prefix = TRUE, link = TRUE, type="Figure")` reveals a left skewed distribution that departs significantly from normality.

**Outliers**: The boxplot in `r kfigr::figr(label = "a_thtr_days_box", prefix = TRUE, link = TRUE, type="Figure")`, which graphically depicts the median, the IQR, and maximum and minimum values, suggested that `r ifelse(nrow(edaUni$thtrDays$outliers) == 0, "no", " ")` outliers were extant. `r edaUni$thtrDays$out` 

### Theatre Days
This variable captured the number of days between theatrical and dvd release

`r kfigr::figr(label = "a_thtr_days_log_stats", prefix = TRUE, link = TRUE, type="Table")`: Log number of theatre days summary statistics
```{r a_thtr_days_log_stats}
knitr::kable(edaUni$thtrDaysLog$stats, digits = 2) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

```{r a_thtr_days_log_dist}
gridExtra::grid.arrange(edaUni$thtrDaysLog$hist, edaUni$thtrDaysLog$qq, ncol = 2)
```
`r kfigr::figr(label = "a_thtr_days_log_dist", prefix = TRUE, link = TRUE, type="Figure")`: Log number of theatre days histogram and QQ Plot

```{r a_thtr_days_log_box, fig.height=4}
edaUni$thtrDaysLog$box
```
`r kfigr::figr(label = "a_thtr_days_log_box", prefix = TRUE, link = TRUE, type="Figure")`: Log number of theatre days boxplot

**Central Tendency**: The summary statistics (`r kfigr::figr(label = "a_thtr_days_log_stats", prefix = TRUE, link = TRUE, type="Table")`) `r edaUni$thtrDaysLog$central`

**Dispersion**: `r edaUni$thtrDaysLog$disp`

**Shape of Distribution**:  `r edaUni$thtrDaysLog$skew` `r edaUni$thtrDaysLog$kurt` The histogram and QQ plot in `r kfigr::figr(label = "a_thtr_days_log_dist", prefix = TRUE, link = TRUE, type="Figure")` reveals a left skewed distribution that departs significantly from normality.

**Outliers**: The boxplot in `r kfigr::figr(label = "a_thtr_days_log_box", prefix = TRUE, link = TRUE, type="Figure")`, which graphically depicts the median, the IQR, and maximum and minimum values, suggested that `r ifelse(nrow(edaUni$thtrDaysLog$outliers) == 0, "no", " ")` outliers were extant. `r edaUni$thtrDaysLog$out` 




## Appendix C: Bivariate Analysis 
## Appendix D: Multivariate Analysis
## Appendix E: Modeling
## Appendix F: Prediction
## Appendix G: Source Code
# References
